---
title: "BESTT_feasibility"
author: "Mark Nwakamma"
date: "09/25/2024"
output: html_document
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(root.dir = "/Users/nwakamma.m/Documents/R-code")

knitr::opts_chunk$set(root.dir = "/Users/marknwakamma/Documents/code_manuscripts/BESTT_feasibility")

library(rlang)
library(patchwork) 
library(ggplot2) 
library(tidyverse)
library(dplyr)
library(psych)
library(nlme)
library(readxl)
library(tidyr)
library(tableone)
library(sjPlot)
library(fmsb)
library(interactions)

Techs <- read_excel("/Users/marknwakamma/Documents/code_manuscripts/BESTT_feasibility/techs_BESTT_final_data.xlsx")
bestt_test <- read_excel("/Users/marknwakamma/Documents/code_manuscripts/BESTT_feasibility/techs_BESTT_final_data.xlsx")
```

## Figure 3 data wrangling
```{r cars}
# heart rate from cycle test
techs_fitness_hr <- Techs %>%
  dplyr::select(name, randomization_group, baseline_hr,hr_2,hr_4,hr_6,hr_7,hr_8,hr_9,hr_10,hr_11)

# change in symptoms from cycle test
techs_fitness_symp <- Techs %>%
  dplyr::select(bestt_severity_change_baseline,bestt_severity_change_2,bestt_severity_change_4,bestt_severity_change_6,bestt_severity_change_7,bestt_severity_change_8,bestt_severity_change_9,bestt_severity_change_10,bestt_severity_change_11)

techs_fitness_numbsymp <- Techs %>%
  dplyr::select(bestt_numb_symps_baseline,bestt_numb_symps_2,bestt_numb_symps_4,bestt_numb_symps_6,bestt_numb_symps_7,bestt_numb_symps_8,bestt_numb_symps_9,bestt_numb_symps_10,bestt_numb_symps_11)


# RPE from cycle test
techs_fitness_rpe <- Techs %>%
  dplyr::select(borg_baseline,borg_2,borg_4,borg_6,borg_7,borg_8,borg_9,borg_10, borg_11)

# Combine heart rate and change in symptoms df
F1_techs <- bind_cols(techs_fitness_hr,techs_fitness_symp,techs_fitness_rpe)
```

```{r}
# Make combined heart rate data long for plotting
F1_techs_hr_long <- F1_techs %>%
  gather(key = "time_point", value = "heart_rate", baseline_hr,hr_2,hr_4,hr_6,hr_7,hr_8,hr_9,hr_10,hr_11)

time_levels <- c("baseline_hr","hr_2","hr_4","hr_6","hr_7","hr_8","hr_9","hr_10","hr_11")

# Convert `time_point` to a factor with specified levels
F1_techs_hr_long <- F1_techs_hr_long %>%
  mutate(time_point = factor(time_point, levels = time_levels))
```

```{r}
# Make combined symptoms change data long for plotting
F1_techs_symp_long <- F1_techs %>% gather(key = "time_point_sym", value = "symp_change", bestt_severity_change_baseline,bestt_severity_change_2,bestt_severity_change_4,bestt_severity_change_6,bestt_severity_change_7,bestt_severity_change_8,bestt_severity_change_9,bestt_severity_change_10,bestt_severity_change_11)

symp_levels <- c("symp_baseline","sympincrease_2","sympincrease_4","sympincrease_6","sympincrease_2_2","sympincrease_2_4","sympincrease_2_6","sympincrease_2_8","sympincrease_2_10")

# Convert `time_point_symp` to a factor with specified levels
F1_techs_symp_long <- F1_techs_symp_long %>%
  mutate(time_point = factor(time_point_sym, levels = symp_levels))
```

```{r}
F1_techs_rpe_long <- F1_techs %>% gather(key = "time_point_rpe", value = "rpe", borg_baseline,borg_2,borg_4,borg_6,borg_7,borg_8,borg_9,borg_10, borg_11)

rpe_levels <- c("borg_baseline","borg_2","borg_4","borg_6","borg_7","borg_8","borg_9","borg_10", "borg_11")

# Convert `time_point_rpe` to a factor with specified levels
F1_techs_rpe_long <- F1_techs_rpe_long %>%
  mutate(time_point = factor(time_point_rpe, levels = rpe_levels))
```

```{r}
# Combine all 3 long datasets
F1_techs <- bind_cols(F1_techs_hr_long,F1_techs_symp_long,F1_techs_rpe_long)

# Create a subset of only variables you will plot
F1_techs <- F1_techs %>% 
  dplyr::select(name...1, time_point...21, heart_rate, symp_change, rpe, randomization_group...2)

F1_techs <- F1_techs %>% 
  dplyr::rename(participant = name...1, timepoint = time_point...21, group = randomization_group...2)
```

```{r}
fit_baseline <- mean(Techs$baseline_hr,na.rm=TRUE)
fit_hrmax_baseline <- mean(Techs$hr_max_baseline,na.rm=TRUE)
fit_symp_baseline <- mean(c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0))
fit_rpe_baseline <- mean(Techs$borg_baseline, na.rm=TRUE)

fit_baseline_2 <- mean(Techs$baseline_hr_2_v1,na.rm=TRUE)
fit_hrmax_baseline_2 <- mean(Techs$hr_max_baseline_2_v1, na.rm=TRUE)
fit_symp_baseline_2 <- mean(Techs$sympincrease_baseline, na.rm=TRUE)
fit_rpe_baseline_2 <- mean(Techs$baseline_borg_2_v1, na.rm=TRUE)

fit_hr2 <- mean(Techs$hr_2,na.rm=TRUE)
fit_hrmax2 <- mean(Techs$hr_max_2,na.rm=TRUE)
fit_symp2 <- mean(Techs$sympincrease_2, na.rm=TRUE)
fit_rpe2 <- mean(Techs$borg_2, na.rm=TRUE)

fit_hr4 <- mean(Techs$hr_4,na.rm=TRUE)
fit_hrmax4 <- mean(Techs$hr_max_4,na.rm=TRUE)
fit_symp4 <- mean(Techs$sympincrease_4, na.rm=TRUE)
fit_rpe4 <- mean(Techs$borg_4, na.rm=TRUE)
fit_hr5 <- mean(Techs$hr_5,na.rm=TRUE)

fit_hr6 <- mean(Techs$hr_6,na.rm=TRUE)
fit_hrmax6 <- mean(Techs$hr_max_6,na.rm=TRUE)
fit_symp6 <- mean(Techs$sympincrease_6, na.rm=TRUE)
fit_rpe6 <- mean(Techs$borg_6, na.rm=TRUE)

fit_hr8 <- mean(Techs$hr_7,na.rm=TRUE)
fit_hrmax8 <- mean(Techs$hr_max_7,na.rm=TRUE)
fit_symp8 <- mean(Techs$sympincrease_2_2, na.rm=TRUE)
fit_rpe8 <- mean(Techs$borg_7, na.rm=TRUE)

fit_hr10 <- mean(Techs$hr_8,na.rm=TRUE)
fit_hrmax10 <- mean(Techs$hr_max_8,na.rm=TRUE)
fit_symp10 <- mean(Techs$sympincrease_2_4, na.rm=TRUE)
fit_rpe10 <- mean(Techs$borg_8, na.rm=TRUE)

fit_hr12 <- mean(Techs$hr_9,na.rm=TRUE)
fit_hrmax12 <- mean(Techs$hr_max_9,na.rm=TRUE)
fit_symp12 <- mean(Techs$sympincrease_2_6, na.rm=TRUE)
fit_rpe12 <- mean(Techs$borg_9, na.rm=TRUE)

fit_hr14 <- mean(Techs$hr_10,na.rm=TRUE)
fit_hrmax14 <- mean(Techs$hr_max_10,na.rm=TRUE)
fit_symp14 <- mean(Techs$sympincrease_2_8, na.rm=TRUE)
fit_rpe14 <- mean(Techs$borg_10, na.rm=TRUE)

fit_hr16 <- mean(Techs$hr_11,na.rm=TRUE)
fit_hrmax16 <- mean(Techs$hr_max_11,na.rm=TRUE)
fit_symp16 <- mean(Techs$sympincrease_2_10, na.rm=TRUE)
fit_rpe16 <- mean(Techs$borg_11, na.rm=TRUE)

fit_hr18 <- mean(Techs$hr_12,na.rm=TRUE)
fit_hrmax18 <- mean(Techs$hr_max_12,na.rm=TRUE)
fit_symp18 <- mean(Techs$sympincrease_2_12, na.rm=TRUE)
fit_rpe18 <- mean(Techs$borg_12, na.rm=TRUE)

fit_heartrate <- c(fit_baseline,fit_baseline_2,fit_hr2, fit_hr4, fit_hr6, fit_hr8,fit_hr10, fit_hr12, fit_hr14, fit_hr16, fit_hr18)

fit_heartratemax <- c(fit_hrmax_baseline,fit_hrmax_baseline_2, fit_hrmax2, fit_hrmax4, fit_hrmax6, fit_hrmax8, fit_hrmax10,fit_hrmax12, fit_hrmax14, fit_hrmax16, fit_hrmax18)

fit_changesymp <- c(fit_symp_baseline,fit_symp_baseline_2,fit_symp2, fit_symp4, fit_symp6, fit_symp8, fit_symp10,fit_symp12, fit_symp14, fit_symp16, fit_symp18)

fit_rpe <- c(fit_rpe_baseline,fit_rpe_baseline_2,fit_rpe2, fit_rpe4, fit_rpe6, fit_rpe8, fit_rpe10,fit_rpe12, fit_rpe14, fit_rpe16, fit_rpe18)

avg_fit_test<- bind_cols(phase,fit_heartrate,fit_heartratemax, fit_changesymp,fit_rpe)

avg_fit_test <- avg_fit_test %>% 
  dplyr::rename(test_phase = ...1, heart_rate = ...2, heart_max = ...3, symp_change = ...4, rpe = ...5)

avg_fit_test <- avg_fit_test %>%
  mutate(test_phase = factor(test_phase, levels = phase))
```


## Plots for baseline symptom distribution
```{r}

# baseline symptom distribution


bestt_test1 <- bestt_test |> 
  mutate(randomization_group = recode(randomization_group,
                                      "0" = "Aerobic Exercise",
                                      "1" = "Balance"))


ggplot2::ggplot(bestt_test1, aes(x = bestt_numb_symps_baseline, fill = randomization_group)) + 
  geom_histogram(binwidth = 1, position = "dodge") + 
  theme_bw() + 
  theme(panel.grid = element_blank(),
        text = element_text(size = 16, family = "Times New Roman"),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "", 
       subtitle = "Distribution of baseline symptoms",
       x = "# of Symptoms", 
       y = "# of Participants") +
  scale_fill_manual(name = "Intervention Group", 
                    values = c("Aerobic Exercise" = "#DA3C00", 
                               "Balance" = "#00A7E1"))

bestt_test |> filter(randomization_group == 0) |> group_by(nausea) |> summarize(n = n())

bestt_test2 <- bestt_test |> 
  select(name, randomization_group, headache, neckpain, dizziness_vomiting, 
         pressure, blurred_vision, balance_problems, light_sensitive, 
         noise_sensitive, slow, fog, feeling_right, concentration, 
         remembering, fatigue, confusion, drowsiness, emotional, 
         irritability, sleep, sadness, anxiety, nausea) |> 
  pivot_longer(cols = -c(name, randomization_group),  # pivot everything except name and group
               names_to = "symptom",
               values_to = "severity") 

# filter for just headache
data <- bestt_test2 |> 
  filter(symptom == "nausea")

# t test comparing headache severity between groups
t.test(baseline_hr ~ randomization_group, data = bestt_test)



```

# Baseline Symptoms radar plot 
```{r}

Techs |> 
  mutate(
    count_headache = sum(headache > 0, na.rm = TRUE),
    mean_nonzero_headache = mean(headache[headache > 0], na.rm = TRUE)
  )

top_symptoms <- data.frame(
    "Headache" = 0.54,
    "Brain fog" = 0.33,
    "Difficulty remembering" = 0.33,
    "Fatigue" = 0.41,
    "Light sensitivity" = 0.33
)

# Define the max and min values
max_min <- data.frame(
    "Headache" = c(1, 0),
    "Brain fog" = c(1, 0),
    "Difficulty remembering" = c(1, 0),
    "Fatigue" = c(1, 0),
    "Light sensitivity" = c(1, 0)
)

# Combine top symptoms with max and min values
top_symptoms_plot <- rbind(max_min, top_symptoms)

# Define the correct axis labels
axis_labels <- seq(0, 1, by = 0.25)

# Create the radar chart
radarchart(
    top_symptoms_plot, axistype = 4,
    # Customizing the plot appearance
    pcol = c("#06A199"),           # Colors for the lines
    pfcol = c(rgb(0.2, 0.5, 0.5, 0.5)), # Colors for the filled areas
    plwd = 3,                      # Line width
    plty = 1,                      # Line type
    cglcol = "grey",               # Color of the grid lines
    cglty = 1,                     # Type of the grid lines
    axislabcol = "black",           # Color of the axis label     # Axis labels
    vlcex = 1                    # Font size for the variable labels
)
```



## Data wrangling of exercise sessions (Figures 4 and 5)
```{r}
Techs$baseline <- rowMeans(Techs[, c("baseline_hr_int1_d5","baseline_hr_int1_d5_d2","baseline_hr_int1_d5_d3","baseline_hr_int1_d5_d4","baseline_hr_int1_d5_d5","baseline_hr_int1_d5_d6","baseline_hr_int1_d5_d7","baseline_hr_int1_d5_d8","baseline_hr_int1_d5_d9","baseline_hr_int1_d5_d10","baseline_hr_int1_d5_d11","baseline_hr_int1_d5_d12","baseline_hr_int1_d5_d13","baseline_hr_int1_d5_d14","baseline_hr_int1_d5_d15","baseline_hr_int1_d5_d16","baseline_hr_int1_d5_d17","baseline_hr_int1_d5_d18","baseline_hr_int1_d5_d19","baseline_hr_int1_d5_d20","baseline_hr_int1_d5_d21","baseline_hr_int1_d5_d22","baseline_hr_int1_d5_d23","baseline_hr_int1_d5_d24","baseline_hr_int1_d5_d25","baseline_hr_int1_d5_d26","baseline_hr_int1_d5_d27","baseline_hr_int1_d5_d28","baseline_hr_int1_d5_d29","baseline_hr_int1_d5_d30","baseline_hr_int1_d5_d31","baseline_hr_int1_d5_d32","baseline_hr_int1_d5_d33","baseline_hr_int1_d5_d34","baseline_hr_int1_d5_d35","baseline_hr_int1_d5_d36")], na.rm=TRUE)

Techs$baseline_hr_perc <- rowMeans(Techs[ , c("hr_max_baseline_int1_d5","hr_max_baseline_int1_d5_d2","hr_max_baseline_int1_d5_d3","hr_max_baseline_int1_d5_d4","hr_max_baseline_int1_d5_d5","hr_max_baseline_int1_d5_d6","hr_max_baseline_int1_d5_d7","hr_max_baseline_int1_d5_d8","hr_max_baseline_int1_d5_d9","hr_max_baseline_int1_d5_d10","hr_max_baseline_int1_d5_d11","hr_max_baseline_int1_d5_d12","hr_max_baseline_int1_d5_d13","hr_max_baseline_int1_d5_d14","hr_max_baseline_int1_d5_d15","hr_max_baseline_int1_d5_d16","hr_max_baseline_int1_d5_d17","hr_max_baseline_int1_d5_d18","hr_max_baseline_int1_d5_d19","hr_max_baseline_int1_d5_d20","hr_max_baseline_int1_d5_d21","hr_max_baseline_int1_d5_d22","hr_max_baseline_int1_d5_d23","hr_max_baseline_int1_d5_d24","hr_max_baseline_int1_d5_d25","hr_max_baseline_int1_d5_d26","hr_max_baseline_int1_d5_d27","hr_max_baseline_int1_d5_d28","hr_max_baseline_int1_d5_d29","hr_max_baseline_int1_d5_d30","hr_max_baseline_int1_d5_d31","hr_max_baseline_int1_d5_d32","hr_max_baseline_int1_d5_d33","hr_max_baseline_int1_d5_d34","hr_max_baseline_int1_d5_d35","hr_max_baseline_int1_d5_d36")], na.rm=TRUE)

Techs$baseline_chng_symp <- rowMeans(Techs[, c("severity_change_int1","severity_change_int1_d2","severity_change_int1_d3", "severity_change_int1_d4", "severity_change_int1_d5","severity_change_int1_d6","severity_change_int1_d7","severity_change_int1_d8","severity_change_int1_d9","severity_change_int1_d10","severity_change_int1_d11","severity_change_int1_d12","severity_change_int1_d13","severity_change_int1_d14","severity_change_int1_d15","severity_change_int1_d16","severity_change_int1_d17","severity_change_int1_d18","severity_change_int1_d19","severity_change_int1_d20","severity_change_int1_d21","severity_change_int1_d22","severity_change_int1_d23","severity_change_int1_d24","severity_change_int1_d25","severity_change_int1_d26","severity_change_int1_d27","severity_change_int1_d28","severity_change_int1_d29","severity_change_int1_d30","severity_change_int1_d31","severity_change_int1_d32","severity_change_int1_d33","severity_change_int1_d34","severity_change_int1_d35","severity_change_int1_d36")], na.rm=TRUE)

Techs$baseline_numb_symps <- rowMeans(Techs[, c("numb_symps_int1","numb_symps_int1_d2","numb_symps_int1_d3","numb_symps_int1_d4", "numb_symps_int1_d5", "numb_symps_int1_d6","numb_symps_int1_d7","numb_symps_int1_d8","numb_symps_int1_d9","numb_symps_int1_d10","numb_symps_int1_d11","numb_symps_int1_d12","numb_symps_int1_d13","numb_symps_int1_d14","numb_symps_int1_d15","numb_symps_int1_d16","numb_symps_int1_d17","numb_symps_int1_d18","numb_symps_int1_d19","numb_symps_int1_d20","numb_symps_int1_d21","numb_symps_int1_d22","numb_symps_int1_d23","numb_symps_int1_d24","numb_symps_int1_d25","numb_symps_int1_d26","numb_symps_int1_d27","numb_symps_int1_d28","numb_symps_int1_d29","numb_symps_int1_d30","numb_symps_int1_d31","numb_symps_int1_d32","numb_symps_int1_d33","numb_symps_int1_d34","numb_symps_int1_d35", "numb_symps_int1_d36")], na.rm=TRUE)

Techs$min05 <- rowMeans(Techs[, c("hr_1_int1_d5","hr_1_int1_d5_d2","hr_1_int1_d5_d3","hr_1_int1_d5_d4","hr_1_int1_d5_d5","hr_1_int1_d5_d6","hr_1_int1_d5_d7","hr_1_int1_d5_d8","hr_1_int1_d5_d9","hr_1_int1_d5_d10","hr_1_int1_d5_d11","hr_1_int1_d5_d12","hr_1_int1_d5_d13","hr_1_int1_d5_d14","hr_1_int1_d5_d15","hr_1_int1_d5_d16","hr_1_int1_d5_d17","hr_1_int1_d5_d18","hr_1_int1_d5_d19","hr_1_int1_d5_d20","hr_1_int1_d5_d21","hr_1_int1_d5_d22","hr_1_int1_d5_d23","hr_1_int1_d5_d24","hr_1_int1_d5_d25","hr_1_int1_d5_d26","hr_1_int1_d5_d27","hr_1_int1_d5_d28","hr_1_int1_d5_d29","hr_1_int1_d5_d30","hr_1_int1_d5_d31","hr_1_int1_d5_d32","hr_1_int1_d5_d33","hr_1_int1_d5_d34","hr_1_int1_d5_d35","hr_1_int1_d5_d36")], na.rm=TRUE)

Techs$min05_hr_perc <- rowMeans(Techs[ , c("hr_max_1_int1_d5","hr_max_1_int1_d5_d2","hr_max_1_int1_d5_d3","hr_max_1_int1_d5_d4","hr_max_1_int1_d5_d5","hr_max_1_int1_d5_d6","hr_max_1_int1_d5_d7","hr_max_1_int1_d5_d8","hr_max_1_int1_d5_d9","hr_max_1_int1_d5_d10","hr_max_1_int1_d5_d11","hr_max_1_int1_d5_d12","hr_max_1_int1_d5_d13","hr_max_1_int1_d5_d14","hr_max_1_int1_d5_d15","hr_max_1_int1_d5_d16","hr_max_1_int1_d5_d17","hr_max_1_int1_d5_d18","hr_max_1_int1_d5_d19","hr_max_1_int1_d5_d20","hr_max_1_int1_d5_d21","hr_max_1_int1_d5_d22","hr_max_1_int1_d5_d23","hr_max_1_int1_d5_d24","hr_max_1_int1_d5_d25","hr_max_1_int1_d5_d26","hr_max_1_int1_d5_d27","hr_max_1_int1_d5_d28","hr_max_1_int1_d5_d29","hr_max_1_int1_d5_d30","hr_max_1_int1_d5_d31","hr_max_1_int1_d5_d32","hr_max_1_int1_d5_d33","hr_max_1_int1_d5_d34","hr_max_1_int1_d5_d35","hr_max_1_int1_d5_d36")], na.rm=TRUE)

Techs$min05_chng_symp <- rowMeans(Techs[, c("severity_change_1_int1","severity_change_1_int1_d2","severity_change_1_int1_d3", "severity_change_1_int1_d4", "severity_change_1_int1_d5","severity_change_1_int1_d6","severity_change_1_int1_d7","severity_change_1_int1_d8","severity_change_1_int1_d9","severity_change_1_int1_d10","severity_change_1_int1_d11","severity_change_1_int1_d12","severity_change_1_int1_d13","severity_change_1_int1_d14","severity_change_1_int1_d15","severity_change_1_int1_d16","severity_change_1_int1_d17","severity_change_1_int1_d18","severity_change_1_int1_d19","severity_change_1_int1_d20","severity_change_1_int1_d21","severity_change_1_int1_d22","severity_change_1_int1_d23","severity_change_1_int1_d24","severity_change_1_int1_d25","severity_change_1_int1_d26","severity_change_1_int1_d27","severity_change_1_int1_d28","severity_change_1_int1_d29","severity_change_1_int1_d30","severity_change_1_int1_d31","severity_change_1_int1_d32","severity_change_1_int1_d33","severity_change_1_int1_d34","severity_change_1_int1_d35","severity_change_1_int1_d36")], na.rm=TRUE)

Techs$min05_numb_symps<- rowMeans(Techs[, c("numb_symps_1_int1","numb_symps_1_int1_d2","numb_symps_1_int1_d3","numb_symps_1_int1_d4", "numb_symps_1_int1_d5", "numb_symps_1_int1_d6","numb_symps_1_int1_d7","numb_symps_1_int1_d8","numb_symps_1_int1_d9","numb_symps_1_int1_d10","numb_symps_1_int1_d11","numb_symps_1_int1_d12","numb_symps_1_int1_d13","numb_symps_1_int1_d14","numb_symps_1_int1_d15","numb_symps_1_int1_d16","numb_symps_1_int1_d17","numb_symps_1_int1_d18","numb_symps_1_int1_d19","numb_symps_1_int1_d20","numb_symps_1_int1_d21","numb_symps_1_int1_d22","numb_symps_1_int1_d23","numb_symps_1_int1_d24","numb_symps_1_int1_d25","numb_symps_1_int1_d26","numb_symps_1_int1_d27","numb_symps_1_int1_d28","numb_symps_1_int1_d29","numb_symps_1_int1_d30","numb_symps_1_int1_d31","numb_symps_1_int1_d32","numb_symps_1_int1_d33","numb_symps_1_int1_d34","numb_symps_1_int1_d35", "numb_symps_1_int1_d36")], na.rm=TRUE)

Techs$min10 <- rowMeans(Techs[, c("hr_2_int1_d5","hr_2_int1_d5_d2","hr_2_int1_d5_d3","hr_2_int1_d5_d4","hr_2_int1_d5_d5","hr_2_int1_d5_d6","hr_2_int1_d5_d7","hr_2_int1_d5_d8","hr_2_int1_d5_d9","hr_2_int1_d5_d10","hr_2_int1_d5_d11","hr_2_int1_d5_d12","hr_2_int1_d5_d13","hr_2_int1_d5_d14","hr_2_int1_d5_d15","hr_2_int1_d5_d16","hr_2_int1_d5_d17","hr_2_int1_d5_d18","hr_2_int1_d5_d19","hr_2_int1_d5_d20","hr_2_int1_d5_d21","hr_2_int1_d5_d22","hr_2_int1_d5_d23","hr_2_int1_d5_d24","hr_2_int1_d5_d25","hr_2_int1_d5_d26","hr_2_int1_d5_d27","hr_2_int1_d5_d28","hr_2_int1_d5_d29","hr_2_int1_d5_d30","hr_2_int1_d5_d31","hr_2_int1_d5_d32","hr_2_int1_d5_d33","hr_2_int1_d5_d34","hr_2_int1_d5_d35","hr_2_int1_d5_d36")], na.rm=TRUE)

Techs$min10_hr_perc <- rowMeans(Techs[ , c("hr_max_2_int1_d5","hr_max_2_int1_d5_d2","hr_max_2_int1_d5_d3","hr_max_2_int1_d5_d4","hr_max_2_int1_d5_d5","hr_max_2_int1_d5_d6","hr_max_2_int1_d5_d7","hr_max_2_int1_d5_d8","hr_max_2_int1_d5_d9","hr_max_2_int1_d5_d10","hr_max_2_int1_d5_d11","hr_max_2_int1_d5_d12","hr_max_2_int1_d5_d13","hr_max_2_int1_d5_d14","hr_max_2_int1_d5_d15","hr_max_2_int1_d5_d16","hr_max_2_int1_d5_d17","hr_max_2_int1_d5_d18","hr_max_2_int1_d5_d19","hr_max_2_int1_d5_d20","hr_max_2_int1_d5_d21","hr_max_2_int1_d5_d22","hr_max_2_int1_d5_d23","hr_max_2_int1_d5_d24","hr_max_2_int1_d5_d25","hr_max_2_int1_d5_d26","hr_max_2_int1_d5_d27","hr_max_2_int1_d5_d28","hr_max_2_int1_d5_d29","hr_max_2_int1_d5_d30","hr_max_2_int1_d5_d31","hr_max_2_int1_d5_d32","hr_max_2_int1_d5_d33","hr_max_2_int1_d5_d34","hr_max_2_int1_d5_d35","hr_max_2_int1_d5_d36")], na.rm=TRUE)

Techs$min10_chng_symp <- rowMeans(Techs[, c("severity_change_2_int1","severity_change_2_int1_d2","severity_change_2_int1_d3", "severity_change_2_int1_d4", "severity_change_2_int1_d5","severity_change_2_int1_d6","severity_change_2_int1_d7","severity_change_2_int1_d8","severity_change_2_int1_d9","severity_change_2_int1_d10","severity_change_2_int1_d11","severity_change_2_int1_d12","severity_change_2_int1_d13","severity_change_2_int1_d14","severity_change_2_int1_d15","severity_change_2_int1_d16","severity_change_2_int1_d17","severity_change_2_int1_d18","severity_change_2_int1_d19","severity_change_2_int1_d20","severity_change_2_int1_d21","severity_change_2_int1_d22","severity_change_2_int1_d23","severity_change_2_int1_d24","severity_change_2_int1_d25","severity_change_2_int1_d26","severity_change_2_int1_d27","severity_change_2_int1_d28","severity_change_2_int1_d29","severity_change_2_int1_d30","severity_change_2_int1_d31","severity_change_2_int1_d32","severity_change_2_int1_d33","severity_change_2_int1_d34","severity_change_2_int1_d35","severity_change_2_int1_d36")], na.rm=TRUE)

Techs$min10_numb_symps <- rowMeans(Techs[, c("numb_symps_2_int1","numb_symps_2_int1_d2","numb_symps_2_int1_d3","numb_symps_2_int1_d4", "numb_symps_2_int1_d5", "numb_symps_2_int1_d6","numb_symps_2_int1_d7","numb_symps_2_int1_d8","numb_symps_2_int1_d9","numb_symps_2_int1_d10","numb_symps_2_int1_d11","numb_symps_2_int1_d12","numb_symps_2_int1_d13","numb_symps_2_int1_d14","numb_symps_2_int1_d15","numb_symps_2_int1_d16","numb_symps_2_int1_d17","numb_symps_2_int1_d18","numb_symps_2_int1_d19","numb_symps_2_int1_d20","numb_symps_2_int1_d21","numb_symps_2_int1_d22","numb_symps_2_int1_d23","numb_symps_2_int1_d24","numb_symps_2_int1_d25","numb_symps_2_int1_d26","numb_symps_2_int1_d27","numb_symps_2_int1_d28","numb_symps_2_int1_d29","numb_symps_2_int1_d30","numb_symps_2_int1_d31","numb_symps_2_int1_d32","numb_symps_2_int1_d33","numb_symps_2_int1_d34","numb_symps_2_int1_d35", "numb_symps_2_int1_d36")], na.rm=TRUE)

Techs$min15 <- rowMeans(Techs[, c("hr_3_int1_d5","hr_3_int1_d5_d2","hr_3_int1_d5_d3","hr_3_int1_d5_d4","hr_3_int1_d5_d5","hr_3_int1_d5_d6","hr_3_int1_d5_d7","hr_3_int1_d5_d8","hr_3_int1_d5_d9","hr_3_int1_d5_d10","hr_3_int1_d5_d11","hr_3_int1_d5_d12","hr_3_int1_d5_d13","hr_3_int1_d5_d14","hr_3_int1_d5_d15","hr_3_int1_d5_d16","hr_3_int1_d5_d17","hr_3_int1_d5_d18","hr_3_int1_d5_d19","hr_3_int1_d5_d20","hr_3_int1_d5_d21","hr_3_int1_d5_d22","hr_3_int1_d5_d23","hr_3_int1_d5_d24","hr_3_int1_d5_d25","hr_3_int1_d5_d26","hr_3_int1_d5_d27","hr_3_int1_d5_d28","hr_3_int1_d5_d29","hr_3_int1_d5_d30","hr_3_int1_d5_d31","hr_3_int1_d5_d32","hr_3_int1_d5_d33","hr_3_int1_d5_d34","hr_3_int1_d5_d35","hr_3_int1_d5_d36")], na.rm=TRUE)

Techs$min15_hr_perc <- rowMeans(Techs[ , c("hr_max_3_int1_d5","hr_max_3_int1_d5_d2","hr_max_3_int1_d5_d3","hr_max_3_int1_d5_d4","hr_max_3_int1_d5_d5","hr_max_3_int1_d5_d6","hr_max_3_int1_d5_d7","hr_max_3_int1_d5_d8","hr_max_3_int1_d5_d9","hr_max_3_int1_d5_d10","hr_max_3_int1_d5_d11","hr_max_3_int1_d5_d12","hr_max_3_int1_d5_d13","hr_max_3_int1_d5_d14","hr_max_3_int1_d5_d15","hr_max_3_int1_d5_d16","hr_max_3_int1_d5_d17","hr_max_3_int1_d5_d18","hr_max_3_int1_d5_d19","hr_max_3_int1_d5_d20","hr_max_3_int1_d5_d21","hr_max_3_int1_d5_d22","hr_max_3_int1_d5_d23","hr_max_3_int1_d5_d24","hr_max_3_int1_d5_d25","hr_max_3_int1_d5_d26","hr_max_3_int1_d5_d27","hr_max_3_int1_d5_d28","hr_max_3_int1_d5_d29","hr_max_3_int1_d5_d30","hr_max_3_int1_d5_d31","hr_max_3_int1_d5_d32","hr_max_3_int1_d5_d33","hr_max_3_int1_d5_d34","hr_max_3_int1_d5_d35","hr_max_3_int1_d5_d36")], na.rm=TRUE)

Techs$min15_chng_symp <- rowMeans(Techs[, c("severity_change_3_int1","severity_change_3_int1_d2","severity_change_3_int1_d3", "severity_change_3_int1_d4", "severity_change_3_int1_d5","severity_change_3_int1_d6","severity_change_3_int1_d7","severity_change_3_int1_d8","severity_change_3_int1_d9","severity_change_3_int1_d10","severity_change_3_int1_d11","severity_change_3_int1_d12","severity_change_3_int1_d13","severity_change_3_int1_d14","severity_change_3_int1_d15","severity_change_3_int1_d16","severity_change_3_int1_d17","severity_change_3_int1_d18","severity_change_3_int1_d19","severity_change_3_int1_d20","severity_change_3_int1_d21","severity_change_3_int1_d22","severity_change_3_int1_d23","severity_change_3_int1_d24","severity_change_3_int1_d25","severity_change_3_int1_d26","severity_change_3_int1_d27","severity_change_3_int1_d28","severity_change_3_int1_d29","severity_change_3_int1_d30","severity_change_3_int1_d31","severity_change_3_int1_d32","severity_change_3_int1_d33","severity_change_3_int1_d34","severity_change_3_int1_d35","severity_change_3_int1_d36")], na.rm=TRUE)

Techs$min15_numb_symps <- rowMeans(Techs[, c("numb_symps_3_int1","numb_symps_3_int1_d2","numb_symps_3_int1_d3","numb_symps_3_int1_d4", "numb_symps_3_int1_d5", "numb_symps_3_int1_d6","numb_symps_3_int1_d7","numb_symps_3_int1_d8","numb_symps_3_int1_d9","numb_symps_3_int1_d10","numb_symps_3_int1_d11","numb_symps_3_int1_d12","numb_symps_3_int1_d13","numb_symps_3_int1_d14","numb_symps_3_int1_d15","numb_symps_3_int1_d16","numb_symps_3_int1_d17","numb_symps_3_int1_d18","numb_symps_3_int1_d19","numb_symps_3_int1_d20","numb_symps_3_int1_d21","numb_symps_3_int1_d22","numb_symps_3_int1_d23","numb_symps_3_int1_d24","numb_symps_3_int1_d25","numb_symps_3_int1_d26","numb_symps_3_int1_d27","numb_symps_3_int1_d28","numb_symps_3_int1_d29","numb_symps_3_int1_d30","numb_symps_3_int1_d31","numb_symps_3_int1_d32","numb_symps_3_int1_d33","numb_symps_3_int1_d34","numb_symps_3_int1_d35", "numb_symps_3_int1_d36")], na.rm=TRUE)

Techs$min20 <- rowMeans(Techs[, c("hr_4_int1_d5","hr_4_int1_d5_d2","hr_4_int1_d5_d3","hr_4_int1_d5_d4","hr_4_int1_d5_d5","hr_4_int1_d5_d6","hr_4_int1_d5_d7","hr_4_int1_d5_d8","hr_4_int1_d5_d9","hr_4_int1_d5_d10","hr_4_int1_d5_d11","hr_4_int1_d5_d12","hr_4_int1_d5_d13","hr_4_int1_d5_d14","hr_4_int1_d5_d15","hr_4_int1_d5_d16","hr_4_int1_d5_d17","hr_4_int1_d5_d18","hr_4_int1_d5_d19","hr_4_int1_d5_d20","hr_4_int1_d5_d21","hr_4_int1_d5_d22","hr_4_int1_d5_d23","hr_4_int1_d5_d24","hr_4_int1_d5_d25","hr_4_int1_d5_d26","hr_4_int1_d5_d27","hr_4_int1_d5_d28","hr_4_int1_d5_d29","hr_4_int1_d5_d30","hr_4_int1_d5_d31","hr_4_int1_d5_d32","hr_4_int1_d5_d33","hr_4_int1_d5_d34","hr_4_int1_d5_d35","hr_4_int1_d5_d36")], na.rm=TRUE)

Techs$min20_hr_perc <- rowMeans(Techs[ , c("hr_max_4_int1_d5","hr_max_4_int1_d5_d2","hr_max_4_int1_d5_d3","hr_max_4_int1_d5_d4","hr_max_4_int1_d5_d5","hr_max_4_int1_d5_d6","hr_max_4_int1_d5_d7","hr_max_4_int1_d5_d8","hr_max_4_int1_d5_d9","hr_max_4_int1_d5_d10","hr_max_4_int1_d5_d11","hr_max_4_int1_d5_d12","hr_max_4_int1_d5_d13","hr_max_4_int1_d5_d14","hr_max_4_int1_d5_d15","hr_max_4_int1_d5_d16","hr_max_4_int1_d5_d17","hr_max_4_int1_d5_d18","hr_max_4_int1_d5_d19","hr_max_4_int1_d5_d20","hr_max_4_int1_d5_d21","hr_max_4_int1_d5_d22","hr_max_4_int1_d5_d23","hr_max_4_int1_d5_d24","hr_max_4_int1_d5_d25","hr_max_4_int1_d5_d26","hr_max_4_int1_d5_d27","hr_max_4_int1_d5_d28","hr_max_4_int1_d5_d29","hr_max_4_int1_d5_d30","hr_max_4_int1_d5_d31","hr_max_4_int1_d5_d32","hr_max_4_int1_d5_d33","hr_max_4_int1_d5_d34","hr_max_4_int1_d5_d35","hr_max_4_int1_d5_d36")], na.rm=TRUE)

Techs$min20_chng_symp <- rowMeans(Techs[, c("severity_change_4_int1","severity_change_4_int1_d2","severity_change_4_int1_d3", "severity_change_4_int1_d4", "severity_change_4_int1_d5","severity_change_4_int1_d6","severity_change_4_int1_d7","severity_change_4_int1_d8","severity_change_4_int1_d9","severity_change_4_int1_d10","severity_change_4_int1_d11","severity_change_4_int1_d12","severity_change_4_int1_d13","severity_change_4_int1_d14","severity_change_4_int1_d15","severity_change_4_int1_d16","severity_change_4_int1_d17","severity_change_4_int1_d18","severity_change_4_int1_d19","severity_change_4_int1_d20","severity_change_4_int1_d21","severity_change_4_int1_d22","severity_change_4_int1_d23","severity_change_4_int1_d24","severity_change_4_int1_d25","severity_change_4_int1_d26","severity_change_4_int1_d27","severity_change_4_int1_d28","severity_change_4_int1_d29","severity_change_4_int1_d30","severity_change_4_int1_d31","severity_change_4_int1_d32","severity_change_4_int1_d33","severity_change_4_int1_d34","severity_change_4_int1_d35","severity_change_4_int1_d36")], na.rm=TRUE)

Techs$min20_numb_symps <- rowMeans(Techs[, c("numb_symps_4_int1","numb_symps_4_int1_d2","numb_symps_4_int1_d3","numb_symps_4_int1_d4", "numb_symps_4_int1_d5", "numb_symps_4_int1_d6","numb_symps_4_int1_d7","numb_symps_4_int1_d8","numb_symps_4_int1_d9","numb_symps_4_int1_d10","numb_symps_4_int1_d11","numb_symps_4_int1_d12","numb_symps_4_int1_d13","numb_symps_4_int1_d14","numb_symps_4_int1_d15","numb_symps_4_int1_d16","numb_symps_4_int1_d17","numb_symps_4_int1_d18","numb_symps_4_int1_d19","numb_symps_4_int1_d20","numb_symps_4_int1_d21","numb_symps_4_int1_d22","numb_symps_4_int1_d23","numb_symps_4_int1_d24","numb_symps_4_int1_d25","numb_symps_4_int1_d26","numb_symps_4_int1_d27","numb_symps_4_int1_d28","numb_symps_4_int1_d29","numb_symps_4_int1_d30","numb_symps_4_int1_d31","numb_symps_4_int1_d32","numb_symps_4_int1_d33","numb_symps_4_int1_d34","numb_symps_4_int1_d35", "numb_symps_4_int1_d36")], na.rm=TRUE)

Techs$min25 <- rowMeans(Techs[, c("hr_5_int1_d5","hr_5_int1_d5_d2","hr_5_int1_d5_d3","hr_5_int1_d5_d4","hr_5_int1_d5_d5","hr_5_int1_d5_d6","hr_5_int1_d5_d7","hr_5_int1_d5_d8","hr_5_int1_d5_d9","hr_5_int1_d5_d10","hr_5_int1_d5_d11","hr_5_int1_d5_d12","hr_5_int1_d5_d13","hr_5_int1_d5_d14","hr_5_int1_d5_d15","hr_5_int1_d5_d16","hr_5_int1_d5_d17","hr_5_int1_d5_d18","hr_5_int1_d5_d19","hr_5_int1_d5_d20","hr_5_int1_d5_d21","hr_5_int1_d5_d22","hr_5_int1_d5_d23","hr_5_int1_d5_d24","hr_5_int1_d5_d25","hr_5_int1_d5_d26","hr_5_int1_d5_d27","hr_5_int1_d5_d28","hr_5_int1_d5_d29","hr_5_int1_d5_d30","hr_5_int1_d5_d31","hr_5_int1_d5_d32","hr_5_int1_d5_d33","hr_5_int1_d5_d34","hr_5_int1_d5_d35","hr_5_int1_d5_d36")], na.rm=TRUE)

Techs$min25_hr_perc <- rowMeans(Techs[ , c("hr_max_5_int1_d5","hr_max_5_int1_d5_d2","hr_max_5_int1_d5_d3","hr_max_5_int1_d5_d4","hr_max_5_int1_d5_d5","hr_max_5_int1_d5_d6","hr_max_5_int1_d5_d7","hr_max_5_int1_d5_d8","hr_max_5_int1_d5_d9","hr_max_5_int1_d5_d10","hr_max_5_int1_d5_d11","hr_max_5_int1_d5_d12","hr_max_5_int1_d5_d13","hr_max_5_int1_d5_d14","hr_max_5_int1_d5_d15","hr_max_5_int1_d5_d16","hr_max_5_int1_d5_d17","hr_max_5_int1_d5_d18","hr_max_5_int1_d5_d19","hr_max_5_int1_d5_d20","hr_max_5_int1_d5_d21","hr_max_5_int1_d5_d22","hr_max_5_int1_d5_d23","hr_max_5_int1_d5_d24","hr_max_5_int1_d5_d25","hr_max_5_int1_d5_d26","hr_max_5_int1_d5_d27","hr_max_5_int1_d5_d28","hr_max_5_int1_d5_d29","hr_max_5_int1_d5_d30","hr_max_5_int1_d5_d31","hr_max_5_int1_d5_d32","hr_max_5_int1_d5_d33","hr_max_5_int1_d5_d34","hr_max_5_int1_d5_d35","hr_max_5_int1_d5_d36")], na.rm=TRUE)

Techs$min25_chng_symp <- rowMeans(Techs[, c("severity_change_5_int1","severity_change_5_int1_d2","severity_change_5_int1_d3", "severity_change_5_int1_d4", "severity_change_5_int1_d5","severity_change_5_int1_d6","severity_change_5_int1_d7","severity_change_5_int1_d8","severity_change_5_int1_d9","severity_change_5_int1_d10","severity_change_5_int1_d11","severity_change_5_int1_d12","severity_change_5_int1_d13","severity_change_5_int1_d14","severity_change_5_int1_d15","severity_change_5_int1_d16","severity_change_5_int1_d17","severity_change_5_int1_d18","severity_change_5_int1_d19","severity_change_5_int1_d20","severity_change_5_int1_d21","severity_change_5_int1_d22","severity_change_5_int1_d23","severity_change_5_int1_d24","severity_change_5_int1_d25","severity_change_5_int1_d26","severity_change_5_int1_d27","severity_change_5_int1_d28","severity_change_5_int1_d29","severity_change_5_int1_d30","severity_change_5_int1_d31","severity_change_5_int1_d32","severity_change_5_int1_d33","severity_change_5_int1_d34","severity_change_5_int1_d35","severity_change_5_int1_d36")], na.rm=TRUE)

Techs$min25_numb_symps <- rowMeans(Techs[, c("numb_symps_5_int1","numb_symps_5_int1_d2","numb_symps_5_int1_d3","numb_symps_5_int1_d4", "numb_symps_5_int1_d5", "numb_symps_5_int1_d6","numb_symps_5_int1_d7","numb_symps_5_int1_d8","numb_symps_5_int1_d9","numb_symps_5_int1_d10","numb_symps_5_int1_d11","numb_symps_5_int1_d12","numb_symps_5_int1_d13","numb_symps_5_int1_d14","numb_symps_5_int1_d15","numb_symps_5_int1_d16","numb_symps_5_int1_d17","numb_symps_5_int1_d18","numb_symps_5_int1_d19","numb_symps_5_int1_d20","numb_symps_5_int1_d21","numb_symps_5_int1_d22","numb_symps_5_int1_d23","numb_symps_5_int1_d24","numb_symps_5_int1_d25","numb_symps_5_int1_d26","numb_symps_5_int1_d27","numb_symps_5_int1_d28","numb_symps_5_int1_d29","numb_symps_5_int1_d30","numb_symps_5_int1_d31","numb_symps_5_int1_d32","numb_symps_5_int1_d33","numb_symps_5_int1_d34","numb_symps_5_int1_d35", "numb_symps_5_int1_d36")], na.rm=TRUE)

Techs$min30 <- rowMeans(Techs[, c("hr_6_int1_d5","hr_6_int1_d5_d2","hr_6_int1_d5_d3","hr_6_int1_d5_d4","hr_6_int1_d5_d5","hr_6_int1_d5_d6","hr_6_int1_d5_d7","hr_6_int1_d5_d8","hr_6_int1_d5_d9","hr_6_int1_d5_d10","hr_6_int1_d5_d11","hr_6_int1_d5_d12","hr_6_int1_d5_d13","hr_6_int1_d5_d14","hr_6_int1_d5_d15","hr_6_int1_d5_d16","hr_6_int1_d5_d17","hr_6_int1_d5_d18","hr_6_int1_d5_d19","hr_6_int1_d5_d20","hr_6_int1_d5_d21","hr_6_int1_d5_d22","hr_6_int1_d5_d23","hr_6_int1_d5_d24","hr_6_int1_d5_d25","hr_6_int1_d5_d26","hr_6_int1_d5_d27","hr_6_int1_d5_d28","hr_6_int1_d5_d29","hr_6_int1_d5_d30","hr_6_int1_d5_d31","hr_6_int1_d5_d32","hr_6_int1_d5_d33","hr_6_int1_d5_d34","hr_6_int1_d5_d35","hr_6_int1_d5_d36")], na.rm=TRUE)

Techs$min30_hr_perc <- rowMeans(Techs[ , c("hr_max_6_int1_d5","hr_max_6_int1_d5_d2","hr_max_6_int1_d5_d3","hr_max_6_int1_d5_d4","hr_max_6_int1_d5_d5","hr_max_6_int1_d5_d6","hr_max_6_int1_d5_d7","hr_max_6_int1_d5_d8","hr_max_6_int1_d5_d9","hr_max_6_int1_d5_d10","hr_max_6_int1_d5_d11","hr_max_6_int1_d5_d12","hr_max_6_int1_d5_d13","hr_max_6_int1_d5_d14","hr_max_6_int1_d5_d15","hr_max_6_int1_d5_d16","hr_max_6_int1_d5_d17","hr_max_6_int1_d5_d18","hr_max_6_int1_d5_d19","hr_max_6_int1_d5_d20","hr_max_6_int1_d5_d21","hr_max_6_int1_d5_d22","hr_max_6_int1_d5_d23","hr_max_6_int1_d5_d24","hr_max_6_int1_d5_d25","hr_max_6_int1_d5_d26","hr_max_6_int1_d5_d27","hr_max_6_int1_d5_d28","hr_max_6_int1_d5_d29","hr_max_6_int1_d5_d30","hr_max_6_int1_d5_d31","hr_max_6_int1_d5_d32","hr_max_6_int1_d5_d33","hr_max_6_int1_d5_d34","hr_max_6_int1_d5_d35","hr_max_6_int1_d5_d36")], na.rm=TRUE)

Techs$min30_chng_symp <- rowMeans(Techs[, c("severity_change_6_int1","severity_change_6_int1_d2","severity_change_6_int1_d3", "severity_change_6_int1_d4", "severity_change_6_int1_d5","severity_change_6_int1_d6","severity_change_6_int1_d7","severity_change_6_int1_d8","severity_change_6_int1_d9","severity_change_6_int1_d10","severity_change_6_int1_d11","severity_change_6_int1_d12","severity_change_6_int1_d13","severity_change_6_int1_d14","severity_change_6_int1_d15","severity_change_6_int1_d16","severity_change_6_int1_d17","severity_change_6_int1_d18","severity_change_6_int1_d19","severity_change_6_int1_d20","severity_change_6_int1_d21","severity_change_6_int1_d22","severity_change_6_int1_d23","severity_change_6_int1_d24","severity_change_6_int1_d25","severity_change_6_int1_d26","severity_change_6_int1_d27","severity_change_6_int1_d28","severity_change_6_int1_d29","severity_change_6_int1_d30","severity_change_6_int1_d31","severity_change_6_int1_d32","severity_change_6_int1_d33","severity_change_6_int1_d34","severity_change_6_int1_d35","severity_change_6_int1_d36")], na.rm=TRUE)

Techs$min30_numb_symps<- rowMeans(Techs[, c("numb_symps_6_int1","numb_symps_6_int1_d2","numb_symps_6_int1_d3","numb_symps_6_int1_d4", "numb_symps_6_int1_d5", "numb_symps_6_int1_d6","numb_symps_6_int1_d7","numb_symps_6_int1_d8","numb_symps_6_int1_d9","numb_symps_6_int1_d10","numb_symps_6_int1_d11","numb_symps_6_int1_d12","numb_symps_6_int1_d13","numb_symps_6_int1_d14","numb_symps_6_int1_d15","numb_symps_6_int1_d16","numb_symps_6_int1_d17","numb_symps_6_int1_d18","numb_symps_6_int1_d19","numb_symps_6_int1_d20","numb_symps_6_int1_d21","numb_symps_6_int1_d22","numb_symps_6_int1_d23","numb_symps_6_int1_d24","numb_symps_6_int1_d25","numb_symps_6_int1_d26","numb_symps_6_int1_d27","numb_symps_6_int1_d28","numb_symps_6_int1_d29","numb_symps_6_int1_d30","numb_symps_6_int1_d31","numb_symps_6_int1_d32","numb_symps_6_int1_d33","numb_symps_6_int1_d34","numb_symps_6_int1_d35", "numb_symps_6_int1_d36")], na.rm=TRUE)
```


## MONTH 1 - data wrangling of exercise sessions
```{r}


Techs$baseline_mon1 <- rowMeans(Techs[, c("baseline_hr_int1_d5","baseline_hr_int1_d5_d2","baseline_hr_int1_d5_d3","baseline_hr_int1_d5_d4","baseline_hr_int1_d5_d5","baseline_hr_int1_d5_d6","baseline_hr_int1_d5_d7","baseline_hr_int1_d5_d8","baseline_hr_int1_d5_d9","baseline_hr_int1_d5_d10","baseline_hr_int1_d5_d11","baseline_hr_int1_d5_d12")], na.rm=TRUE)

Techs$baseline_hr_perc_mon1 <- rowMeans(Techs[ , c("hr_max_baseline_int1_d5","hr_max_baseline_int1_d5_d2","hr_max_baseline_int1_d5_d3","hr_max_baseline_int1_d5_d4","hr_max_baseline_int1_d5_d5","hr_max_baseline_int1_d5_d6","hr_max_baseline_int1_d5_d7","hr_max_baseline_int1_d5_d8","hr_max_baseline_int1_d5_d9","hr_max_baseline_int1_d5_d10","hr_max_baseline_int1_d5_d11","hr_max_baseline_int1_d5_d12")], na.rm=TRUE)

Techs$baseline_chng_symp_mon1 <- rowMeans(Techs[, c("severity_change_int1","severity_change_int1_d2","severity_change_int1_d3", "severity_change_int1_d4", "severity_change_int1_d5","severity_change_int1_d6","severity_change_int1_d7","severity_change_int1_d8","severity_change_int1_d9","severity_change_int1_d10","severity_change_int1_d11","severity_change_int1_d12")], na.rm=TRUE)

Techs$baseline_numb_symps_mon1 <- rowMeans(Techs[, c("numb_symps_int1","numb_symps_int1_d2","numb_symps_int1_d3","numb_symps_int1_d4", "numb_symps_int1_d5", "numb_symps_int1_d6","numb_symps_int1_d7","numb_symps_int1_d8","numb_symps_int1_d9","numb_symps_int1_d10","numb_symps_int1_d11","numb_symps_int1_d12")], na.rm=TRUE)

Techs$min05_mon1 <- rowMeans(Techs[, c("hr_1_int1_d5","hr_1_int1_d5_d2","hr_1_int1_d5_d3","hr_1_int1_d5_d4","hr_1_int1_d5_d5","hr_1_int1_d5_d6","hr_1_int1_d5_d7","hr_1_int1_d5_d8","hr_1_int1_d5_d9","hr_1_int1_d5_d10","hr_1_int1_d5_d11","hr_1_int1_d5_d12")], na.rm=TRUE)

Techs$min05_hr_perc_mon1 <- rowMeans(Techs[ , c("hr_max_1_int1_d5","hr_max_1_int1_d5_d2","hr_max_1_int1_d5_d3","hr_max_1_int1_d5_d4","hr_max_1_int1_d5_d5","hr_max_1_int1_d5_d6","hr_max_1_int1_d5_d7","hr_max_1_int1_d5_d8","hr_max_1_int1_d5_d9","hr_max_1_int1_d5_d10","hr_max_1_int1_d5_d11","hr_max_1_int1_d5_d12")], na.rm=TRUE)

Techs$min05_chng_symp_mon1 <- rowMeans(Techs[, c("severity_change_1_int1","severity_change_1_int1_d2","severity_change_1_int1_d3", "severity_change_1_int1_d4", "severity_change_1_int1_d5","severity_change_1_int1_d6","severity_change_1_int1_d7","severity_change_1_int1_d8","severity_change_1_int1_d9","severity_change_1_int1_d10","severity_change_1_int1_d11","severity_change_1_int1_d12")], na.rm=TRUE)

Techs$min05_numb_symps_mon1 <- rowMeans(Techs[, c("numb_symps_1_int1","numb_symps_1_int1_d2","numb_symps_1_int1_d3","numb_symps_1_int1_d4", "numb_symps_1_int1_d5", "numb_symps_1_int1_d6","numb_symps_1_int1_d7","numb_symps_1_int1_d8","numb_symps_1_int1_d9","numb_symps_1_int1_d10","numb_symps_1_int1_d11","numb_symps_1_int1_d12")], na.rm=TRUE)

Techs$min10_mon1 <- rowMeans(Techs[, c("hr_2_int1_d5","hr_2_int1_d5_d2","hr_2_int1_d5_d3","hr_2_int1_d5_d4","hr_2_int1_d5_d5","hr_2_int1_d5_d6","hr_2_int1_d5_d7","hr_2_int1_d5_d8","hr_2_int1_d5_d9","hr_2_int1_d5_d10","hr_2_int1_d5_d11","hr_2_int1_d5_d12")], na.rm=TRUE)

Techs$min10_hr_perc_mon1 <- rowMeans(Techs[ , c("hr_max_2_int1_d5","hr_max_2_int1_d5_d2","hr_max_2_int1_d5_d3","hr_max_2_int1_d5_d4","hr_max_2_int1_d5_d5","hr_max_2_int1_d5_d6","hr_max_2_int1_d5_d7","hr_max_2_int1_d5_d8","hr_max_2_int1_d5_d9","hr_max_2_int1_d5_d10","hr_max_2_int1_d5_d11","hr_max_2_int1_d5_d12")], na.rm=TRUE)

Techs$min10_chng_symp_mon1 <- rowMeans(Techs[, c("severity_change_2_int1","severity_change_2_int1_d2","severity_change_2_int1_d3", "severity_change_2_int1_d4", "severity_change_2_int1_d5","severity_change_2_int1_d6","severity_change_2_int1_d7","severity_change_2_int1_d8","severity_change_2_int1_d9","severity_change_2_int1_d10","severity_change_2_int1_d11","severity_change_2_int1_d12")], na.rm=TRUE)

Techs$min10_numb_symps_mon1 <- rowMeans(Techs[, c("numb_symps_2_int1","numb_symps_2_int1_d2","numb_symps_2_int1_d3","numb_symps_2_int1_d4", "numb_symps_2_int1_d5", "numb_symps_2_int1_d6","numb_symps_2_int1_d7","numb_symps_2_int1_d8","numb_symps_2_int1_d9","numb_symps_2_int1_d10","numb_symps_2_int1_d11","numb_symps_2_int1_d12")], na.rm=TRUE)

Techs$min15_mon1 <- rowMeans(Techs[, c("hr_3_int1_d5","hr_3_int1_d5_d2","hr_3_int1_d5_d3","hr_3_int1_d5_d4","hr_3_int1_d5_d5","hr_3_int1_d5_d6","hr_3_int1_d5_d7","hr_3_int1_d5_d8","hr_3_int1_d5_d9","hr_3_int1_d5_d10","hr_3_int1_d5_d11","hr_3_int1_d5_d12")], na.rm=TRUE)

Techs$min15_hr_perc_mon1 <- rowMeans(Techs[ , c("hr_max_3_int1_d5","hr_max_3_int1_d5_d2","hr_max_3_int1_d5_d3","hr_max_3_int1_d5_d4","hr_max_3_int1_d5_d5","hr_max_3_int1_d5_d6","hr_max_3_int1_d5_d7","hr_max_3_int1_d5_d8","hr_max_3_int1_d5_d9","hr_max_3_int1_d5_d10","hr_max_3_int1_d5_d11","hr_max_3_int1_d5_d12")], na.rm=TRUE)

Techs$min15_chng_symp_mon1 <- rowMeans(Techs[, c("severity_change_3_int1","severity_change_3_int1_d2","severity_change_3_int1_d3", "severity_change_3_int1_d4", "severity_change_3_int1_d5","severity_change_3_int1_d6","severity_change_3_int1_d7","severity_change_3_int1_d8","severity_change_3_int1_d9","severity_change_3_int1_d10","severity_change_3_int1_d11","severity_change_3_int1_d12")], na.rm=TRUE)

Techs$min15_numb_symps_mon1 <- rowMeans(Techs[, c("numb_symps_3_int1","numb_symps_3_int1_d2","numb_symps_3_int1_d3","numb_symps_3_int1_d4", "numb_symps_3_int1_d5", "numb_symps_3_int1_d6","numb_symps_3_int1_d7","numb_symps_3_int1_d8","numb_symps_3_int1_d9","numb_symps_3_int1_d10","numb_symps_3_int1_d11","numb_symps_3_int1_d12")], na.rm=TRUE)

Techs$min20_mon1 <- rowMeans(Techs[, c("hr_4_int1_d5","hr_4_int1_d5_d2","hr_4_int1_d5_d3","hr_4_int1_d5_d4","hr_4_int1_d5_d5","hr_4_int1_d5_d6","hr_4_int1_d5_d7","hr_4_int1_d5_d8","hr_4_int1_d5_d9","hr_4_int1_d5_d10","hr_4_int1_d5_d11","hr_4_int1_d5_d12")], na.rm=TRUE)

Techs$min20_hr_perc_mon1 <- rowMeans(Techs[ , c("hr_max_4_int1_d5","hr_max_4_int1_d5_d2","hr_max_4_int1_d5_d3","hr_max_4_int1_d5_d4","hr_max_4_int1_d5_d5","hr_max_4_int1_d5_d6","hr_max_4_int1_d5_d7","hr_max_4_int1_d5_d8","hr_max_4_int1_d5_d9","hr_max_4_int1_d5_d10","hr_max_4_int1_d5_d11","hr_max_4_int1_d5_d12")], na.rm=TRUE)

Techs$min20_chng_symp_mon1 <- rowMeans(Techs[, c("severity_change_4_int1","severity_change_4_int1_d2","severity_change_4_int1_d3", "severity_change_4_int1_d4", "severity_change_4_int1_d5","severity_change_4_int1_d6","severity_change_4_int1_d7","severity_change_4_int1_d8","severity_change_4_int1_d9","severity_change_4_int1_d10","severity_change_4_int1_d11","severity_change_4_int1_d12")], na.rm=TRUE)

Techs$min20_numb_symps_mon1 <- rowMeans(Techs[, c("numb_symps_4_int1","numb_symps_4_int1_d2","numb_symps_4_int1_d3","numb_symps_4_int1_d4", "numb_symps_4_int1_d5", "numb_symps_4_int1_d6","numb_symps_4_int1_d7","numb_symps_4_int1_d8","numb_symps_4_int1_d9","numb_symps_4_int1_d10","numb_symps_4_int1_d11","numb_symps_4_int1_d12")], na.rm=TRUE)

Techs$min25_mon1 <- rowMeans(Techs[, c("hr_5_int1_d5","hr_5_int1_d5_d2","hr_5_int1_d5_d3","hr_5_int1_d5_d4","hr_5_int1_d5_d5","hr_5_int1_d5_d6","hr_5_int1_d5_d7","hr_5_int1_d5_d8","hr_5_int1_d5_d9","hr_5_int1_d5_d10","hr_5_int1_d5_d11","hr_5_int1_d5_d12")], na.rm=TRUE)

Techs$min25_hr_perc_mon1 <- rowMeans(Techs[ , c("hr_max_5_int1_d5","hr_max_5_int1_d5_d2","hr_max_5_int1_d5_d3","hr_max_5_int1_d5_d4","hr_max_5_int1_d5_d5","hr_max_5_int1_d5_d6","hr_max_5_int1_d5_d7","hr_max_5_int1_d5_d8","hr_max_5_int1_d5_d9","hr_max_5_int1_d5_d10","hr_max_5_int1_d5_d11","hr_max_5_int1_d5_d12")], na.rm=TRUE)

Techs$min25_chng_symp_mon1 <- rowMeans(Techs[, c("severity_change_5_int1","severity_change_5_int1_d2","severity_change_5_int1_d3", "severity_change_5_int1_d4", "severity_change_5_int1_d5","severity_change_5_int1_d6","severity_change_5_int1_d7","severity_change_5_int1_d8","severity_change_5_int1_d9","severity_change_5_int1_d10","severity_change_5_int1_d11","severity_change_5_int1_d12")], na.rm=TRUE)

Techs$min25_numb_symps_mon1 <- rowMeans(Techs[, c("numb_symps_5_int1","numb_symps_5_int1_d2","numb_symps_5_int1_d3","numb_symps_5_int1_d4", "numb_symps_5_int1_d5", "numb_symps_5_int1_d6","numb_symps_5_int1_d7","numb_symps_5_int1_d8","numb_symps_5_int1_d9","numb_symps_5_int1_d10","numb_symps_5_int1_d11","numb_symps_5_int1_d12")], na.rm=TRUE)

Techs$min30_mon1 <- rowMeans(Techs[, c("hr_6_int1_d5","hr_6_int1_d5_d2","hr_6_int1_d5_d3","hr_6_int1_d5_d4","hr_6_int1_d5_d5","hr_6_int1_d5_d6","hr_6_int1_d5_d7","hr_6_int1_d5_d8","hr_6_int1_d5_d9","hr_6_int1_d5_d10","hr_6_int1_d5_d11","hr_6_int1_d5_d12")], na.rm=TRUE)

Techs$min30_hr_perc_mon1 <- rowMeans(Techs[ , c("hr_max_6_int1_d5","hr_max_6_int1_d5_d2","hr_max_6_int1_d5_d3","hr_max_6_int1_d5_d4","hr_max_6_int1_d5_d5","hr_max_6_int1_d5_d6","hr_max_6_int1_d5_d7","hr_max_6_int1_d5_d8","hr_max_6_int1_d5_d9","hr_max_6_int1_d5_d10","hr_max_6_int1_d5_d11","hr_max_6_int1_d5_d12")], na.rm=TRUE)

Techs$min30_chng_symp_mon1 <- rowMeans(Techs[, c("severity_change_6_int1","severity_change_6_int1_d2","severity_change_6_int1_d3", "severity_change_6_int1_d4", "severity_change_6_int1_d5","severity_change_6_int1_d6","severity_change_6_int1_d7","severity_change_6_int1_d8","severity_change_6_int1_d9","severity_change_6_int1_d10","severity_change_6_int1_d11","severity_change_6_int1_d12")], na.rm=TRUE)

Techs$min30_numb_symps_mon1 <- rowMeans(Techs[, c("numb_symps_6_int1","numb_symps_6_int1_d2","numb_symps_6_int1_d3","numb_symps_6_int1_d4", "numb_symps_6_int1_d5", "numb_symps_6_int1_d6","numb_symps_6_int1_d7","numb_symps_6_int1_d8","numb_symps_6_int1_d9","numb_symps_6_int1_d10","numb_symps_6_int1_d11","numb_symps_6_int1_d12")], na.rm=TRUE)
```


## MONTH 2 - data wrangling of exercise sessions
```{r}


Techs$baseline_mon2 <- rowMeans(Techs[, c("baseline_hr_int1_d5_d13","baseline_hr_int1_d5_d14","baseline_hr_int1_d5_d15","baseline_hr_int1_d5_d16","baseline_hr_int1_d5_d17","baseline_hr_int1_d5_d18","baseline_hr_int1_d5_d19","baseline_hr_int1_d5_d20","baseline_hr_int1_d5_d21","baseline_hr_int1_d5_d22","baseline_hr_int1_d5_d23","baseline_hr_int1_d5_d24")], na.rm=TRUE)

Techs$baseline_hr_perc_mon2 <- rowMeans(Techs[ , c("hr_max_baseline_int1_d5_d13","hr_max_baseline_int1_d5_d14","hr_max_baseline_int1_d5_d15","hr_max_baseline_int1_d5_d16","hr_max_baseline_int1_d5_d17","hr_max_baseline_int1_d5_d18","hr_max_baseline_int1_d5_d19","hr_max_baseline_int1_d5_d20","hr_max_baseline_int1_d5_d21","hr_max_baseline_int1_d5_d22","hr_max_baseline_int1_d5_d23","hr_max_baseline_int1_d5_d24")], na.rm=TRUE)

Techs$baseline_chng_symp_mon2 <- rowMeans(Techs[, c("severity_change_int1_d13","severity_change_int1_d14","severity_change_int1_d15","severity_change_int1_d16","severity_change_int1_d17","severity_change_int1_d18","severity_change_int1_d19","severity_change_int1_d20","severity_change_int1_d21","severity_change_int1_d22","severity_change_int1_d23","severity_change_int1_d24")], na.rm=TRUE)

Techs$baseline_numb_symps_mon2 <- rowMeans(Techs[, c("numb_symps_int1_d13","numb_symps_int1_d14","numb_symps_int1_d15","numb_symps_int1_d16","numb_symps_int1_d17","numb_symps_int1_d18","numb_symps_int1_d19","numb_symps_int1_d20","numb_symps_int1_d21","numb_symps_int1_d22","numb_symps_int1_d23","numb_symps_int1_d24")], na.rm=TRUE)

Techs$min05_mon2 <- rowMeans(Techs[, c("hr_1_int1_d5_d13","hr_1_int1_d5_d14","hr_1_int1_d5_d15","hr_1_int1_d5_d16","hr_1_int1_d5_d17","hr_1_int1_d5_d18","hr_1_int1_d5_d19","hr_1_int1_d5_d20","hr_1_int1_d5_d21","hr_1_int1_d5_d22","hr_1_int1_d5_d23","hr_1_int1_d5_d24")], na.rm=TRUE)

Techs$min05_hr_perc_mon2 <- rowMeans(Techs[ , c("hr_max_1_int1_d5_d13","hr_max_1_int1_d5_d14","hr_max_1_int1_d5_d15","hr_max_1_int1_d5_d16","hr_max_1_int1_d5_d17","hr_max_1_int1_d5_d18","hr_max_1_int1_d5_d19","hr_max_1_int1_d5_d20","hr_max_1_int1_d5_d21","hr_max_1_int1_d5_d22","hr_max_1_int1_d5_d23","hr_max_1_int1_d5_d24")], na.rm=TRUE)

Techs$min05_chng_symp_mon2 <- rowMeans(Techs[, c("severity_change_1_int1_d13","severity_change_1_int1_d14","severity_change_1_int1_d15","severity_change_1_int1_d16","severity_change_1_int1_d17","severity_change_1_int1_d18","severity_change_1_int1_d19","severity_change_1_int1_d20","severity_change_1_int1_d21","severity_change_1_int1_d22","severity_change_1_int1_d23","severity_change_1_int1_d24")], na.rm=TRUE)

Techs$min05_numb_symps_mon2 <- rowMeans(Techs[, c("numb_symps_1_int1_d13","numb_symps_1_int1_d14","numb_symps_1_int1_d15","numb_symps_1_int1_d16","numb_symps_1_int1_d17","numb_symps_1_int1_d18","numb_symps_1_int1_d19","numb_symps_1_int1_d20","numb_symps_1_int1_d21","numb_symps_1_int1_d22","numb_symps_1_int1_d23","numb_symps_1_int1_d24")], na.rm=TRUE)

Techs$min10_mon2 <- rowMeans(Techs[, c("hr_2_int1_d5_d13","hr_2_int1_d5_d14","hr_2_int1_d5_d15","hr_2_int1_d5_d16","hr_2_int1_d5_d17","hr_2_int1_d5_d18","hr_2_int1_d5_d19","hr_2_int1_d5_d20","hr_2_int1_d5_d21","hr_2_int1_d5_d22","hr_2_int1_d5_d23","hr_2_int1_d5_d24")], na.rm=TRUE)

Techs$min10_hr_perc_mon2 <- rowMeans(Techs[ , c("hr_max_2_int1_d5_d13","hr_max_2_int1_d5_d14","hr_max_2_int1_d5_d15","hr_max_2_int1_d5_d16","hr_max_2_int1_d5_d17","hr_max_2_int1_d5_d18","hr_max_2_int1_d5_d19","hr_max_2_int1_d5_d20","hr_max_2_int1_d5_d21","hr_max_2_int1_d5_d22","hr_max_2_int1_d5_d23","hr_max_2_int1_d5_d24")], na.rm=TRUE)

Techs$min10_chng_symp_mon2 <- rowMeans(Techs[, c("severity_change_2_int1_d13","severity_change_2_int1_d14","severity_change_2_int1_d15","severity_change_2_int1_d16","severity_change_2_int1_d17","severity_change_2_int1_d18","severity_change_2_int1_d19","severity_change_2_int1_d20","severity_change_2_int1_d21","severity_change_2_int1_d22","severity_change_2_int1_d23","severity_change_2_int1_d24")], na.rm=TRUE)

Techs$min10_numb_symps_mon2 <- rowMeans(Techs[, c("numb_symps_2_int1_d13","numb_symps_2_int1_d14","numb_symps_2_int1_d15","numb_symps_2_int1_d16","numb_symps_2_int1_d17","numb_symps_2_int1_d18","numb_symps_2_int1_d19","numb_symps_2_int1_d20","numb_symps_2_int1_d21","numb_symps_2_int1_d22","numb_symps_2_int1_d23","numb_symps_2_int1_d24")], na.rm=TRUE)

Techs$min15_mon2 <- rowMeans(Techs[, c("hr_3_int1_d5_d13","hr_3_int1_d5_d14","hr_3_int1_d5_d15","hr_3_int1_d5_d16","hr_3_int1_d5_d17","hr_3_int1_d5_d18","hr_3_int1_d5_d19","hr_3_int1_d5_d20","hr_3_int1_d5_d21","hr_3_int1_d5_d22","hr_3_int1_d5_d23","hr_3_int1_d5_d24")], na.rm=TRUE)

Techs$min15_hr_perc_mon2 <- rowMeans(Techs[ , c("hr_max_3_int1_d5_d13","hr_max_3_int1_d5_d14","hr_max_3_int1_d5_d15","hr_max_3_int1_d5_d16","hr_max_3_int1_d5_d17","hr_max_3_int1_d5_d18","hr_max_3_int1_d5_d19","hr_max_3_int1_d5_d20","hr_max_3_int1_d5_d21","hr_max_3_int1_d5_d22","hr_max_3_int1_d5_d23","hr_max_3_int1_d5_d24")], na.rm=TRUE)

Techs$min15_chng_symp_mon2 <- rowMeans(Techs[, c("severity_change_3_int1_d13","severity_change_3_int1_d14","severity_change_3_int1_d15","severity_change_3_int1_d16","severity_change_3_int1_d17","severity_change_3_int1_d18","severity_change_3_int1_d19","severity_change_3_int1_d20","severity_change_3_int1_d21","severity_change_3_int1_d22","severity_change_3_int1_d23","severity_change_3_int1_d24")], na.rm=TRUE)

Techs$min15_numb_symps_mon2 <- rowMeans(Techs[, c("numb_symps_3_int1_d13","numb_symps_3_int1_d14","numb_symps_3_int1_d15","numb_symps_3_int1_d16","numb_symps_3_int1_d17","numb_symps_3_int1_d18","numb_symps_3_int1_d19","numb_symps_3_int1_d20","numb_symps_3_int1_d21","numb_symps_3_int1_d22","numb_symps_3_int1_d23","numb_symps_3_int1_d24")], na.rm=TRUE)

Techs$min20_mon2 <- rowMeans(Techs[, c("hr_4_int1_d5_d13","hr_4_int1_d5_d14","hr_4_int1_d5_d15","hr_4_int1_d5_d16","hr_4_int1_d5_d17","hr_4_int1_d5_d18","hr_4_int1_d5_d19","hr_4_int1_d5_d20","hr_4_int1_d5_d21","hr_4_int1_d5_d22","hr_4_int1_d5_d23","hr_4_int1_d5_d24")], na.rm=TRUE)

Techs$min20_hr_perc_mon2 <- rowMeans(Techs[ , c("hr_max_4_int1_d5_d13","hr_max_4_int1_d5_d14","hr_max_4_int1_d5_d15","hr_max_4_int1_d5_d16","hr_max_4_int1_d5_d17","hr_max_4_int1_d5_d18","hr_max_4_int1_d5_d19","hr_max_4_int1_d5_d20","hr_max_4_int1_d5_d21","hr_max_4_int1_d5_d22","hr_max_4_int1_d5_d23","hr_max_4_int1_d5_d24")], na.rm=TRUE)

Techs$min20_chng_symp_mon2 <- rowMeans(Techs[, c("severity_change_4_int1_d13","severity_change_4_int1_d14","severity_change_4_int1_d15","severity_change_4_int1_d16","severity_change_4_int1_d17","severity_change_4_int1_d18","severity_change_4_int1_d19","severity_change_4_int1_d20","severity_change_4_int1_d21","severity_change_4_int1_d22","severity_change_4_int1_d23","severity_change_4_int1_d24")], na.rm=TRUE)

Techs$min20_numb_symps_mon2 <- rowMeans(Techs[, c("numb_symps_4_int1_d13","numb_symps_4_int1_d14","numb_symps_4_int1_d15","numb_symps_4_int1_d16","numb_symps_4_int1_d17","numb_symps_4_int1_d18","numb_symps_4_int1_d19","numb_symps_4_int1_d20","numb_symps_4_int1_d21","numb_symps_4_int1_d22","numb_symps_4_int1_d23","numb_symps_4_int1_d24")], na.rm=TRUE)

Techs$min25_mon2 <- rowMeans(Techs[, c("hr_5_int1_d5_d13","hr_5_int1_d5_d14","hr_5_int1_d5_d15","hr_5_int1_d5_d16","hr_5_int1_d5_d17","hr_5_int1_d5_d18","hr_5_int1_d5_d19","hr_5_int1_d5_d20","hr_5_int1_d5_d21","hr_5_int1_d5_d22","hr_5_int1_d5_d23","hr_5_int1_d5_d24")], na.rm=TRUE)

Techs$min25_hr_perc_mon2 <- rowMeans(Techs[ , c("hr_max_5_int1_d5_d13","hr_max_5_int1_d5_d14","hr_max_5_int1_d5_d15","hr_max_5_int1_d5_d16","hr_max_5_int1_d5_d17","hr_max_5_int1_d5_d18","hr_max_5_int1_d5_d19","hr_max_5_int1_d5_d20","hr_max_5_int1_d5_d21","hr_max_5_int1_d5_d22","hr_max_5_int1_d5_d23","hr_max_5_int1_d5_d24")], na.rm=TRUE)

Techs$min25_chng_symp_mon2 <- rowMeans(Techs[, c("severity_change_5_int1_d13","severity_change_5_int1_d14","severity_change_5_int1_d15","severity_change_5_int1_d16","severity_change_5_int1_d17","severity_change_5_int1_d18","severity_change_5_int1_d19","severity_change_5_int1_d20","severity_change_5_int1_d21","severity_change_5_int1_d22","severity_change_5_int1_d23","severity_change_5_int1_d24")], na.rm=TRUE)

Techs$min25_numb_symps_mon2 <- rowMeans(Techs[, c("numb_symps_5_int1_d13","numb_symps_5_int1_d14","numb_symps_5_int1_d15","numb_symps_5_int1_d16","numb_symps_5_int1_d17","numb_symps_5_int1_d18","numb_symps_5_int1_d19","numb_symps_5_int1_d20","numb_symps_5_int1_d21","numb_symps_5_int1_d22","numb_symps_5_int1_d23","numb_symps_5_int1_d24")], na.rm=TRUE)

Techs$min30_mon2 <- rowMeans(Techs[, c("hr_6_int1_d5_d13","hr_6_int1_d5_d14","hr_6_int1_d5_d15","hr_6_int1_d5_d16","hr_6_int1_d5_d17","hr_6_int1_d5_d18","hr_6_int1_d5_d19","hr_6_int1_d5_d20","hr_6_int1_d5_d21","hr_6_int1_d5_d22","hr_6_int1_d5_d23","hr_6_int1_d5_d24")], na.rm=TRUE)

Techs$min30_hr_perc_mon2 <- rowMeans(Techs[ , c("hr_max_6_int1_d5_d13","hr_max_6_int1_d5_d14","hr_max_6_int1_d5_d15","hr_max_6_int1_d5_d16","hr_max_6_int1_d5_d17","hr_max_6_int1_d5_d18","hr_max_6_int1_d5_d19","hr_max_6_int1_d5_d20","hr_max_6_int1_d5_d21","hr_max_6_int1_d5_d22","hr_max_6_int1_d5_d23","hr_max_6_int1_d5_d24")], na.rm=TRUE)

Techs$min30_chng_symp_mon2 <- rowMeans(Techs[, c("severity_change_6_int1_d13","severity_change_6_int1_d14","severity_change_6_int1_d15","severity_change_6_int1_d16","severity_change_6_int1_d17","severity_change_6_int1_d18","severity_change_6_int1_d19","severity_change_6_int1_d20","severity_change_6_int1_d21","severity_change_6_int1_d22","severity_change_6_int1_d23","severity_change_6_int1_d24")], na.rm=TRUE)

Techs$min30_numb_symps_mon2 <- rowMeans(Techs[, c("numb_symps_6_int1_d13","numb_symps_6_int1_d14","numb_symps_6_int1_d15","numb_symps_6_int1_d16","numb_symps_6_int1_d17","numb_symps_6_int1_d18","numb_symps_6_int1_d19","numb_symps_6_int1_d20","numb_symps_6_int1_d21","numb_symps_6_int1_d22","numb_symps_6_int1_d23","numb_symps_6_int1_d24")], na.rm=TRUE)
```


## MONTH 3 - data wrangling of exercise sessions
```{r}


Techs$baseline_mon3 <- rowMeans(Techs[, c("baseline_hr_int1_d5_d25","baseline_hr_int1_d5_d26","baseline_hr_int1_d5_d27","baseline_hr_int1_d5_d28","baseline_hr_int1_d5_d29","baseline_hr_int1_d5_d30","baseline_hr_int1_d5_d31","baseline_hr_int1_d5_d32","baseline_hr_int1_d5_d33","baseline_hr_int1_d5_d34","baseline_hr_int1_d5_d35","baseline_hr_int1_d5_d36")], na.rm=TRUE)

Techs$baseline_hr_perc_mon3 <- rowMeans(Techs[ , c("hr_max_baseline_int1_d5_d25","hr_max_baseline_int1_d5_d26","hr_max_baseline_int1_d5_d27","hr_max_baseline_int1_d5_d28","hr_max_baseline_int1_d5_d29","hr_max_baseline_int1_d5_d30","hr_max_baseline_int1_d5_d31","hr_max_baseline_int1_d5_d32","hr_max_baseline_int1_d5_d33","hr_max_baseline_int1_d5_d34","hr_max_baseline_int1_d5_d35","hr_max_baseline_int1_d5_d36")], na.rm=TRUE)

Techs$baseline_chng_symp_mon3 <- rowMeans(Techs[, c("severity_change_int1_d25","severity_change_int1_d26","severity_change_int1_d27","severity_change_int1_d28","severity_change_int1_d29","severity_change_int1_d30","severity_change_int1_d31","severity_change_int1_d32","severity_change_int1_d33","severity_change_int1_d34","severity_change_int1_d35","severity_change_int1_d36")], na.rm=TRUE)

Techs$baseline_numb_symps_mon3 <- rowMeans(Techs[, c("numb_symps_int1_d25","numb_symps_int1_d26","numb_symps_int1_d27","numb_symps_int1_d28","numb_symps_int1_d29","numb_symps_int1_d30","numb_symps_int1_d31","numb_symps_int1_d32","numb_symps_int1_d33","numb_symps_int1_d34","numb_symps_int1_d35", "numb_symps_int1_d36")], na.rm=TRUE)

Techs$min05_mon3 <- rowMeans(Techs[, c("hr_1_int1_d5_d25","hr_1_int1_d5_d26","hr_1_int1_d5_d27","hr_1_int1_d5_d28","hr_1_int1_d5_d29","hr_1_int1_d5_d30","hr_1_int1_d5_d31","hr_1_int1_d5_d32","hr_1_int1_d5_d33","hr_1_int1_d5_d34","hr_1_int1_d5_d35","hr_1_int1_d5_d36")], na.rm=TRUE)

Techs$min05_hr_perc_mon3 <- rowMeans(Techs[ , c("hr_max_1_int1_d5_d25","hr_max_1_int1_d5_d26","hr_max_1_int1_d5_d27","hr_max_1_int1_d5_d28","hr_max_1_int1_d5_d29","hr_max_1_int1_d5_d30","hr_max_1_int1_d5_d31","hr_max_1_int1_d5_d32","hr_max_1_int1_d5_d33","hr_max_1_int1_d5_d34","hr_max_1_int1_d5_d35","hr_max_1_int1_d5_d36")], na.rm=TRUE)

Techs$min05_chng_symp_mon3 <- rowMeans(Techs[, c("severity_change_1_int1_d25","severity_change_1_int1_d26","severity_change_1_int1_d27","severity_change_1_int1_d28","severity_change_1_int1_d29","severity_change_1_int1_d30","severity_change_1_int1_d31","severity_change_1_int1_d32","severity_change_1_int1_d33","severity_change_1_int1_d34","severity_change_1_int1_d35","severity_change_1_int1_d36")], na.rm=TRUE)

Techs$min05_numb_symps_mon3 <- rowMeans(Techs[, c("numb_symps_1_int1_d25","numb_symps_1_int1_d26","numb_symps_1_int1_d27","numb_symps_1_int1_d28","numb_symps_1_int1_d29","numb_symps_1_int1_d30","numb_symps_1_int1_d31","numb_symps_1_int1_d32","numb_symps_1_int1_d33","numb_symps_1_int1_d34","numb_symps_1_int1_d35", "numb_symps_1_int1_d36")], na.rm=TRUE)

Techs$min10_mon3 <- rowMeans(Techs[, c("hr_2_int1_d5_d25","hr_2_int1_d5_d26","hr_2_int1_d5_d27","hr_2_int1_d5_d28","hr_2_int1_d5_d29","hr_2_int1_d5_d30","hr_2_int1_d5_d31","hr_2_int1_d5_d32","hr_2_int1_d5_d33","hr_2_int1_d5_d34","hr_2_int1_d5_d35","hr_2_int1_d5_d36")], na.rm=TRUE)

Techs$min10_hr_perc_mon3 <- rowMeans(Techs[ , c("hr_max_2_int1_d5_d25","hr_max_2_int1_d5_d26","hr_max_2_int1_d5_d27","hr_max_2_int1_d5_d28","hr_max_2_int1_d5_d29","hr_max_2_int1_d5_d30","hr_max_2_int1_d5_d31","hr_max_2_int1_d5_d32","hr_max_2_int1_d5_d33","hr_max_2_int1_d5_d34","hr_max_2_int1_d5_d35","hr_max_2_int1_d5_d36")], na.rm=TRUE)

Techs$min10_chng_symp_mon3 <- rowMeans(Techs[, c("severity_change_2_int1_d25","severity_change_2_int1_d26","severity_change_2_int1_d27","severity_change_2_int1_d28","severity_change_2_int1_d29","severity_change_2_int1_d30","severity_change_2_int1_d31","severity_change_2_int1_d32","severity_change_2_int1_d33","severity_change_2_int1_d34","severity_change_2_int1_d35","severity_change_2_int1_d36")], na.rm=TRUE)

Techs$min10_numb_symps_mon3 <- rowMeans(Techs[, c("numb_symps_2_int1_d25","numb_symps_2_int1_d26","numb_symps_2_int1_d27","numb_symps_2_int1_d28","numb_symps_2_int1_d29","numb_symps_2_int1_d30","numb_symps_2_int1_d31","numb_symps_2_int1_d32","numb_symps_2_int1_d33","numb_symps_2_int1_d34","numb_symps_2_int1_d35", "numb_symps_2_int1_d36")], na.rm=TRUE)

Techs$min15_mon3 <- rowMeans(Techs[, c("hr_3_int1_d5_d25","hr_3_int1_d5_d26","hr_3_int1_d5_d27","hr_3_int1_d5_d28","hr_3_int1_d5_d29","hr_3_int1_d5_d30","hr_3_int1_d5_d31","hr_3_int1_d5_d32","hr_3_int1_d5_d33","hr_3_int1_d5_d34","hr_3_int1_d5_d35","hr_3_int1_d5_d36")], na.rm=TRUE)

Techs$min15_hr_perc_mon3 <- rowMeans(Techs[ , c("hr_max_3_int1_d5_d25","hr_max_3_int1_d5_d26","hr_max_3_int1_d5_d27","hr_max_3_int1_d5_d28","hr_max_3_int1_d5_d29","hr_max_3_int1_d5_d30","hr_max_3_int1_d5_d31","hr_max_3_int1_d5_d32","hr_max_3_int1_d5_d33","hr_max_3_int1_d5_d34","hr_max_3_int1_d5_d35","hr_max_3_int1_d5_d36")], na.rm=TRUE)

Techs$min15_chng_symp_mon3 <- rowMeans(Techs[, c("severity_change_3_int1_d25","severity_change_3_int1_d26","severity_change_3_int1_d27","severity_change_3_int1_d28","severity_change_3_int1_d29","severity_change_3_int1_d30","severity_change_3_int1_d31","severity_change_3_int1_d32","severity_change_3_int1_d33","severity_change_3_int1_d34","severity_change_3_int1_d35","severity_change_3_int1_d36")], na.rm=TRUE)

Techs$min15_numb_symps_mon3 <- rowMeans(Techs[, c("numb_symps_3_int1_d25","numb_symps_3_int1_d26","numb_symps_3_int1_d27","numb_symps_3_int1_d28","numb_symps_3_int1_d29","numb_symps_3_int1_d30","numb_symps_3_int1_d31","numb_symps_3_int1_d32","numb_symps_3_int1_d33","numb_symps_3_int1_d34","numb_symps_3_int1_d35", "numb_symps_3_int1_d36")], na.rm=TRUE)

Techs$min20_mon3 <- rowMeans(Techs[, c("hr_4_int1_d5_d25","hr_4_int1_d5_d26","hr_4_int1_d5_d27","hr_4_int1_d5_d28","hr_4_int1_d5_d29","hr_4_int1_d5_d30","hr_4_int1_d5_d31","hr_4_int1_d5_d32","hr_4_int1_d5_d33","hr_4_int1_d5_d34","hr_4_int1_d5_d35","hr_4_int1_d5_d36")], na.rm=TRUE)

Techs$min20_hr_perc_mon3 <- rowMeans(Techs[ , c("hr_max_4_int1_d5_d25","hr_max_4_int1_d5_d26","hr_max_4_int1_d5_d27","hr_max_4_int1_d5_d28","hr_max_4_int1_d5_d29","hr_max_4_int1_d5_d30","hr_max_4_int1_d5_d31","hr_max_4_int1_d5_d32","hr_max_4_int1_d5_d33","hr_max_4_int1_d5_d34","hr_max_4_int1_d5_d35","hr_max_4_int1_d5_d36")], na.rm=TRUE)

Techs$min20_chng_symp_mon3 <- rowMeans(Techs[, c("severity_change_4_int1_d25","severity_change_4_int1_d26","severity_change_4_int1_d27","severity_change_4_int1_d28","severity_change_4_int1_d29","severity_change_4_int1_d30","severity_change_4_int1_d31","severity_change_4_int1_d32","severity_change_4_int1_d33","severity_change_4_int1_d34","severity_change_4_int1_d35","severity_change_4_int1_d36")], na.rm=TRUE)

Techs$min20_numb_symps_mon3 <- rowMeans(Techs[, c("numb_symps_4_int1_d25","numb_symps_4_int1_d26","numb_symps_4_int1_d27","numb_symps_4_int1_d28","numb_symps_4_int1_d29","numb_symps_4_int1_d30","numb_symps_4_int1_d31","numb_symps_4_int1_d32","numb_symps_4_int1_d33","numb_symps_4_int1_d34","numb_symps_4_int1_d35", "numb_symps_4_int1_d36")], na.rm=TRUE)

Techs$min25_mon3 <- rowMeans(Techs[, c("hr_5_int1_d5_d25","hr_5_int1_d5_d26","hr_5_int1_d5_d27","hr_5_int1_d5_d28","hr_5_int1_d5_d29","hr_5_int1_d5_d30","hr_5_int1_d5_d31","hr_5_int1_d5_d32","hr_5_int1_d5_d33","hr_5_int1_d5_d34","hr_5_int1_d5_d35","hr_5_int1_d5_d36")], na.rm=TRUE)

Techs$min25_hr_perc_mon3 <- rowMeans(Techs[ , c("hr_max_5_int1_d5_d25","hr_max_5_int1_d5_d26","hr_max_5_int1_d5_d27","hr_max_5_int1_d5_d28","hr_max_5_int1_d5_d29","hr_max_5_int1_d5_d30","hr_max_5_int1_d5_d31","hr_max_5_int1_d5_d32","hr_max_5_int1_d5_d33","hr_max_5_int1_d5_d34","hr_max_5_int1_d5_d35","hr_max_5_int1_d5_d36")], na.rm=TRUE)

Techs$min25_chng_symp_mon3 <- rowMeans(Techs[, c("severity_change_5_int1_d25","severity_change_5_int1_d26","severity_change_5_int1_d27","severity_change_5_int1_d28","severity_change_5_int1_d29","severity_change_5_int1_d30","severity_change_5_int1_d31","severity_change_5_int1_d32","severity_change_5_int1_d33","severity_change_5_int1_d34","severity_change_5_int1_d35","severity_change_5_int1_d36")], na.rm=TRUE)

Techs$min25_numb_symps_mon3 <- rowMeans(Techs[, c("numb_symps_5_int1_d25","numb_symps_5_int1_d26","numb_symps_5_int1_d27","numb_symps_5_int1_d28","numb_symps_5_int1_d29","numb_symps_5_int1_d30","numb_symps_5_int1_d31","numb_symps_5_int1_d32","numb_symps_5_int1_d33","numb_symps_5_int1_d34","numb_symps_5_int1_d35", "numb_symps_5_int1_d36")], na.rm=TRUE)

Techs$min30_mon3 <- rowMeans(Techs[, c("hr_6_int1_d5_d25","hr_6_int1_d5_d26","hr_6_int1_d5_d27","hr_6_int1_d5_d28","hr_6_int1_d5_d29","hr_6_int1_d5_d30","hr_6_int1_d5_d31","hr_6_int1_d5_d32","hr_6_int1_d5_d33","hr_6_int1_d5_d34","hr_6_int1_d5_d35","hr_6_int1_d5_d36")], na.rm=TRUE)

Techs$min30_hr_perc_mon3 <- rowMeans(Techs[ , c("hr_max_6_int1_d5_d25","hr_max_6_int1_d5_d26","hr_max_6_int1_d5_d27","hr_max_6_int1_d5_d28","hr_max_6_int1_d5_d29","hr_max_6_int1_d5_d30","hr_max_6_int1_d5_d31","hr_max_6_int1_d5_d32","hr_max_6_int1_d5_d33","hr_max_6_int1_d5_d34","hr_max_6_int1_d5_d35","hr_max_6_int1_d5_d36")], na.rm=TRUE)

Techs$min30_chng_symp_mon3 <- rowMeans(Techs[, c("severity_change_6_int1_d25","severity_change_6_int1_d26","severity_change_6_int1_d27","severity_change_6_int1_d28","severity_change_6_int1_d29","severity_change_6_int1_d30","severity_change_6_int1_d31","severity_change_6_int1_d32","severity_change_6_int1_d33","severity_change_6_int1_d34","severity_change_6_int1_d35","severity_change_6_int1_d36")], na.rm=TRUE)

Techs$min30_numb_symps_mon3<- rowMeans(Techs[, c("numb_symps_6_int1_d25","numb_symps_6_int1_d26","numb_symps_6_int1_d27","numb_symps_6_int1_d28","numb_symps_6_int1_d29","numb_symps_6_int1_d30","numb_symps_6_int1_d31","numb_symps_6_int1_d32","numb_symps_6_int1_d33","numb_symps_6_int1_d34","numb_symps_6_int1_d35", "numb_symps_6_int1_d36")], na.rm=TRUE)
```


## Creaing data sets for modifiers of HR x symptom severity
```{r} 
 Techs <- Techs %>% 
dplyr::rename(participant = name)

 # 'active' vs 'non-active' based on ACSM PA recommendations
Techs_athl_set <- Techs
Techs_athl_set <- Techs_athl_set |> mutate(baseline_vig_and_mod = baseline_vig_min_per_day_pa + baseline_mod_min_pa)
hist(Techs_athl_set$baseline_vig_and_mod)
Techs_athl_set$baseline_vig_and_mod <- if_else(Techs_athl_set$baseline_vig_and_mod > 75,0, 1)

# fit (above poor) vs. non fit (at or below poor VO2 scores)
Techs_fit_set <- Techs
hist(Techs$relative_vo2max_agecorrected_baseline)
Techs_fit_set$relative_vo2max_agecorrected_baseline <- if_else(Techs_fit_set$relative_vo2max_agecorrected_baseline > 37.4065,0, 1)

# under 25 vs over 25 years old
Techs_age_set <- Techs
hist(Techs$age)
Techs_age_set$age <- if_else(Techs_age_set$age > 27,0,1)

# within 8 weeks vs over 8 weeks since injury
Techs_tbi_set <- Techs
hist(Techs$days_since_injury_calc)
Techs_tbi_set$days_since_injury_calc <- if_else(Techs_tbi_set$days_since_injury_calc > 44.5,0, 1)

```

# Long formatted datasets for each data set to look at 12-week intervention
```{r}

# CHANGE IN HEART RATE
long_techs1 <- Techs %>%
gather(key = "time_point", value = "heart_rate", baseline, min05, min10, min15, min20, min25, min30) 

long_techs1_perc <- Techs %>%
gather(key = "time_point", value = "heart_rate_perc", baseline_hr_perc, min05_hr_perc, min10_hr_perc, min15_hr_perc, min20_hr_perc, min25_hr_perc, min30_hr_perc)

long_techs1 <- long_techs1 %>% dplyr::select(participant, adherence, randomization_group, time_point, heart_rate, maxhr_65, maxhr_80)

long_techs1_perc <- long_techs1_perc %>% dplyr::select(heart_rate_perc)

long_techs1 <- bind_cols(long_techs1,long_techs1_perc)

long_techs1_mon1 <- Techs %>%
gather(key = "time_point", value = "heart_rate_mon1", baseline_mon1, min05_mon1, min10_mon1, min15_mon1, min20_mon1, min25_mon1, min30_mon1)

long_techs1_mon1 <- long_techs1_mon1 %>% dplyr::select(heart_rate_mon1)

long_techs1_mon2 <- Techs %>%
gather(key = "time_point", value = "heart_rate_mon2", baseline_mon2, min05_mon2, min10_mon2, min15_mon2, min20_mon2, min25_mon2, min30_mon2)

long_techs1_mon2 <- long_techs1_mon2 %>% dplyr::select(heart_rate_mon2)

long_techs1_mon3 <- Techs %>%
gather(key = "time_point", value = "heart_rate_mon3", baseline_mon3, min05_mon3, min10_mon3, min15_mon3, min20_mon3, min25_mon3, min30_mon3)

long_techs1_mon3 <- long_techs1_mon3 %>% dplyr::select(heart_rate_mon3)

long_techs1 <- bind_cols(long_techs1, long_techs1_mon1,long_techs1_mon2,long_techs1_mon3)


# CHANGE IN SYMPTOMS
long_techs2 <- Techs %>%
  gather(key = "timepoint", value = "symptom_change",baseline_chng_symp, min05_chng_symp, min10_chng_symp, min15_chng_symp, min20_chng_symp, min25_chng_symp, min30_chng_symp)

long_techs2 <- long_techs2 %>% dplyr::select(symptom_change)

long_techs2_mon1 <- Techs %>%
  gather(key = "timepoint", value = "symptom_change_mon1",baseline_chng_symp_mon1, min05_chng_symp_mon1, min10_chng_symp_mon1, min15_chng_symp_mon1, min20_chng_symp_mon1, min25_chng_symp_mon1, min30_chng_symp_mon1)

long_techs2_mon1 <- long_techs2_mon1 %>% dplyr::select(symptom_change_mon1)

long_techs2_mon2 <- Techs %>%
  gather(key = "timepoint", value = "symptom_change_mon2",baseline_chng_symp_mon2, min05_chng_symp_mon2, min10_chng_symp_mon2, min15_chng_symp_mon2, min20_chng_symp_mon2, min25_chng_symp_mon2, min30_chng_symp_mon2)

long_techs2_mon2 <- long_techs2_mon2 %>% dplyr::select(symptom_change_mon2)

long_techs2_mon3 <- Techs %>%
  gather(key = "timepoint", value = "symptom_change_mon3",baseline_chng_symp_mon3, min05_chng_symp_mon3, min10_chng_symp_mon3, min15_chng_symp_mon3, min20_chng_symp_mon3, min25_chng_symp_mon3, min30_chng_symp_mon3)

long_techs2_mon3 <- long_techs2_mon3 %>% dplyr::select(symptom_change_mon3)

long_techs2 <- bind_cols(long_techs2, long_techs2_mon1,long_techs2_mon2,long_techs2_mon3)

# COMBINE INTO ONE DATAFRAME

long_techs <- bind_cols(long_techs1, long_techs2)

#long_techs <- long_techs[-c(25,26,51,52,77,78,103,104,129,130,155,156,181,182),]

long_techs <- long_techs[long_techs$randomization_group == 1,]

phase <- c("baseline", "phase1_2min", "phase1_4min", "phase1_6min", "phase2_2min", "phase2_4min", "phase2_6min", "phase2_8min", "phase2_10min")

time_main <- c("baseline", "min05", "min10", "min15", "min20", "min25", "min30")

```


## Modifiers - Long formatted datasets for each data set to look at 12-week intervention
``` {r}
long_techs1.1 <- Techs_athl_set %>%
gather(key = "time_point", value = "heart_rate", baseline, min05, min10, min15, min20, min25, min30)

long_techs1.2 <- Techs_fit_set %>%
gather(key = "time_point", value = "heart_rate", baseline, min05, min10, min15, min20, min25, min30)

long_techs1.3 <- Techs_age_set %>%
gather(key = "time_point", value = "heart_rate", baseline, min05, min10, min15, min20, min25, min30)

long_techs1.4 <- Techs_tbi_set %>%
gather(key = "time_point", value = "heart_rate", baseline, min05, min10, min15, min20, min25, min30)

long_techs1.1 <- long_techs1.1 %>% dplyr::select(participant, randomization_group, baseline_vig_and_mod, time_point, heart_rate, maxhr_65, maxhr_80) # need to add change in symptoms from interventions

long_techs1.2 <- long_techs1.2 %>%
dplyr::select(participant, randomization_group,relative_vo2max_agecorrected_baseline, time_point, heart_rate, maxhr_65, maxhr_80) # need to add change in symptoms from interventions

long_techs1.3 <- long_techs1.3 %>%
dplyr::select(participant, randomization_group,age, time_point, heart_rate, maxhr_65, maxhr_80) # need to add change in symptoms from interventions and age

long_techs1.4 <- long_techs1.4 %>%
dplyr::select(participant, randomization_group, days_since_injury_calc, time_point, heart_rate, maxhr_65, maxhr_80) # need to add change in symptoms from interventions and days since injury

long_techs_sub <- bind_cols(long_techs1.4, long_techs2)

long_techs_sub <- long_techs_sub[long_techs_sub$randomization_group == 0,]

long_techs_sub <- long_techs_sub[long_techs_sub$days_since_injury_calc == 1,]

```


## Demographics table
```{r}

# Demographics using tableone function
# sex was manually accounted for
vars <- c("age", "years_of_ed", "days_since_injury", "num_symp_baseline")
group_vars <- "group"
demo_table <- CreateTableOne(vars = vars, data = Techs, addOverall = TRUE)

print(demo_table)
```

## Baseline symptom distribution
```{r}
Techs$randomization_group <- as.factor(Techs$randomization_group)

ggplot2::ggplot(Techs, mapping = aes(x = baseline_cif)) + geom_histogram(mapping = aes(fill= randomization_group)) + theme_bw()+ theme( panel.grid = element_blank()) + theme(text = element_text(size = 16, family = "Times New Roman")) + scale_fill_manual(name = "Group",labels=c("Aerobic", "Balance"), values = c("#d55e00", "#0072b2")) + 
  labs(title = "", 
              subtitle = "Distribution of baseline symptoms",
              x = "# of Symptoms", y = "# of participants") + theme(plot.subtitle = element_text(hjust = 0.5))
```


## MEBT - whole sample
```{r}
ggplot(F1_techs, aes(x = timepoint)) +
  geom_line(aes(group = participant, y = heart_rate, color = "#339E76"), alpha = 0.25, size = 0.5, na.rm = TRUE) +
  geom_point(aes(group = participant, y = heart_rate, color = "#339E76"), alpha = 0.25, size = 0.5, na.rm = TRUE) +
  geom_line(aes(group = participant, y = symp_change*10, color = "#C36521"), alpha = 0.25, size = 0.5, na.rm = TRUE) + 
  geom_point(aes(group = participant, y = symp_change*10, color = "#C36521"), alpha = 0.25, size = 0.5, na.rm = TRUE) + 
  scale_y_continuous(name = "Heart rate", limits = c(-50, 200),
    sec.axis = sec_axis(~./10, name = "Change in Symptoms", breaks = seq(-6,12,by = 3))) +
  scale_x_discrete(name = "Time Point", labels = phase) +
   stat_summary(aes(y = heart_rate, group = 1, color = "#f57600"), fun = mean, geom = "line", size = 1.5, na.rm = TRUE, linetype = "solid") +
  stat_summary(aes(y = symp_change*10, group = 1,color = "blue"), fun = mean, geom = "line", size = 1.5, na.rm = TRUE, linetype = "solid") + theme_minimal() + 
  theme(
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1), 
    legend.position = "none", 
    legend.key.size = unit(0.5, "cm"),  # Smaller legend keys
    legend.text = element_text(size = 8),  # Smaller legend text
    legend.title = element_text(size = 10),  # Smaller legend title
    text = element_text(size= 12,family = "Times New Roman"),
    plot.margin = margin(t = 15, r = 15, b = 15, l = 10),
    axis.title.y.right = element_text(margin = margin(l = 10))) + 
  labs(x = "Time Point", y = "Change in symptoms", subtitle = "Heart rate & ∆ in symptoms during MEBT") + 
  geom_segment(aes(x = 4, xend = 4 , y = -50, yend = 200), size = 0.5, color = "black", linetype = "dashed") + 
  geom_segment(aes(x = 0, xend = 10 , y = 30, yend = 30), size = 0.5, color = "black", linetype = "dashed")
```



## MEBT - split by group
```{r}

F1_techs_group <- F1_techs |>
  dplyr::mutate(
    group = factor(group, levels = c(0, 1), labels = c("Aerobic Exercise", "Balance")),
    timepoint = dplyr::recode(timepoint,
                    "baseline_hr" = "Baseline",
                    "hr_2" = "Phase1: 2min",
                   "hr_4" = "Phase1: 4min",
                   "hr_6" = "Phase1: 6min",
                   "hr_7" = "Phase2: 8min",
                   "hr_8" = "Phase2: 10min",
                   "hr_9" = "Phase2: 12min",
                   "hr_10" = "Phase2: 14min",
                   "hr_11" = "Phase2: 16min")
                   )


F1_techs_group = F1_techs_group[-c(201,211),]

ggplot(F1_techs_group, aes(x = timepoint)) +
  geom_line(aes(group = participant, y = heart_rate, color = group), alpha = 0.25, size = 0.5, na.rm = TRUE) +
  geom_point(aes(group = participant, y = heart_rate, color = group), alpha = 0.25, size = 0.5, na.rm = TRUE) +
  geom_line(aes(group = participant, y = symp_change*10, color = group), alpha = 0.25, size = 0.5, na.rm = TRUE) + 
  geom_point(aes(group = participant, y = symp_change*10, color = group), alpha = 0.25, size = 0.5, na.rm = TRUE) + 
  scale_y_continuous(name = "Heart rate", limits = c(-50, 200),
    sec.axis = sec_axis(~./10, name = "Change in Symptoms", breaks = seq(-6,12,by = 3))) +
# Aerobic group mean lines - full length
  stat_summary(data = F1_techs_group %>% filter(group == "Aerobic Exercise"),
               aes(y = heart_rate, group = group, color = group), 
               fun = mean, geom = "line", size = 1.5, na.rm = TRUE, linetype = "solid") +
  stat_summary(data = F1_techs_group %>% filter(group == "Aerobic Exercise"),
               aes(y = symp_change*10, group = group, color = group), 
               fun = mean, geom = "line", size = 1.5, na.rm = TRUE, linetype = "solid") +

  # Balance group mean lines - stopping one timepoint earlier
  stat_summary(data = F1_techs_group %>% filter(group == "Balance" & timepoint != "Phase2: 16min"), aes(y = heart_rate, group = group, color = group), fun = mean, geom = "line", size = 1.5, na.rm = TRUE, linetype = "solid") +
  stat_summary(data = F1_techs_group %>% filter(group == "Balance" & timepoint != "Phase2: 16min"), aes(y = symp_change*10, group = group, color = group), 
               fun = mean, geom = "line", size = 1.5, na.rm = TRUE, linetype = "solid") +
scale_color_manual(name = "Intervention group", values = c("Aerobic Exercise" = "#FC7569", "Balance" = "#00C0C5")) + 
  
  theme_minimal() + 
  theme(
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1), 
    legend.position = "right", 
    legend.key.size = unit(0.5, "cm"),  # Smaller legend keys
    legend.text = element_text(size = 8),  # Smaller legend text
    legend.title = element_text(size = 10),  # Smaller legend title
    text = element_text(size= 12,family = "Times New Roman"),
    plot.margin = margin(t = 15, r = 15, b = 15, l = 10),
    axis.title.y.right = element_text(margin = margin(l = 10))) + 
  labs(x = "Time Point", y = "Change in symptoms", subtitle = "Heart rate & ∆ in symptoms during MEBT by intervention") + 
  geom_segment(aes(x = 4, xend = 4 , y = -50, yend = 200), size = 0.5, color = "black", linetype = "dashed") + 
  geom_segment(aes(x = 0, xend = 10 , y = 30, yend = 30), size = 0.5, color = "black", linetype = "dashed")
```


## Exercise intervention by participant
```{r}

long_techs_main <- long_techs |>
  dplyr::mutate(
    timepoint = factor(time_point, levels = time_main),
    randomization_group = factor(randomization_group, levels = c(0, 1), labels = c("Aerobic Exercise", "Balance"))
  )

ggplot(long_techs_main, aes(x = time_point)) +
  geom_line(aes(group = participant, y = heart_rate, color = randomization_group), alpha = 0.25, size = 0.5, na.rm = TRUE) +
  geom_point(aes(group = participant, y = heart_rate, color = randomization_group), alpha = 0.25, size = 0.5, na.rm = TRUE) +
  geom_line(aes(group = participant, y = symptom_change*17, color = randomization_group), alpha = 0.25, size = 0.5, na.rm = TRUE) + 
  geom_point(aes(group = participant, y = symptom_change*17, color = randomization_group), alpha = 0.25, size = 0.5, na.rm = TRUE) + 
  scale_y_continuous(name = "Heart rate", limits = c(-50, 200),
    sec.axis = sec_axis(~./17, name = "Change in Symptoms", breaks = seq(-6,12,by = 3))) +
  scale_x_discrete(name = "Time Point", labels = time_main) +
  stat_summary(aes(y = heart_rate, group = randomization_group, color = randomization_group), fun = mean, geom = "line", size = 1.5, na.rm = TRUE, linetype = "solid") +
  stat_summary(aes(y = symptom_change*10, group = randomization_group, color = randomization_group), fun = mean, geom = "line", size = 1.5, na.rm = TRUE, linetype = "solid") + scale_color_manual(name = "Intervention group", values = c("Aerobic Exercise" = "#DA3C00", "Balance" = "#00A7E1")) +
  theme_minimal() + 
  theme(
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1), 
    legend.position = "right", 
    legend.key.size = unit(0.5, "cm"),  # Smaller legend keys
    legend.text = element_text(size = 8),  # Smaller legend text
    legend.title = element_text(size = 10),  # Smaller legend title
    text = element_text(size= 12,family = "Helvetica"),
    plot.margin = margin(t = 15, r = 15, b = 15, l = 10),
    axis.title.y.right = element_text(margin = margin(l = 10))) + 
  labs(x = "Time Point", y = "Change in symptoms", subtitle = "Mean heart rate & ∆ in symptoms following 12-week intervention") + 
  geom_segment(aes(x = 0.5, xend = 8 , y = 50, yend = 50), size = 0.5, color = "black", linetype = "dashed")
```


## RPE and heart rate over time - mixed effects model
```{r}

F1_techs_lme <- F1_techs %>%
  dplyr::mutate(timepoint = dplyr::recode(timepoint,
                   "baseline_hr" = 1,
                   "hr_2" = 2,
                   "hr_4" = 3,
                   "hr_6" = 4,
                   "hr_7" = 5,
                   "hr_8" = 6,
                   "hr_9" = 7,
                   "hr_10" = 8,
                   "hr_11" = 9))

# This model is preferred. Significant chi-square
F1_techs_lme$timepoint <- as.numeric(F1_techs_lme$timepoint)

rpe_heartrate_coef <- lmerTest::lmer(rpe ~ heart_rate + timepoint + (1 + heart_rate|participant), data = F1_techs_lme)

summary(rpe_heartrate_coef)

tab_model(rpe_heartrate_coef, digits = 3, digits.re = 3, show.df = TRUE, df.method = "satterthwaite")

intercepts <- coef(rpe_heartrate_coef)$participant[,1]
intercept <- mean(intercepts)
slopes <- coef(rpe_heartrate_coef)$participant[,2]
slope <- mean(slopes)


abline_data <- data.frame(participant = rownames(coef(rpe_heartrate_coef)$participant), intercepts = intercepts, slopes = slopes)

# RPE X Heart rate plot for all participants
ggplot(F1_techs_lme, aes(x=heart_rate, y=rpe, group = participant)) +
  geom_point() +  
  geom_abline(slope = slope, intercept = intercept, size = 3, color = "#f57600") + # slopes for different participants
  geom_abline(data = abline_data, aes(slope=slopes, intercept=intercepts), alpha = 0.25) + 
  theme(panel.background = element_blank() ,                                                                   panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA),
          legend.position = "none",
        text = element_text(size= 12, family = "Times New Roman")) +
  labs(subtitle = "Rate of perceived exertion x Heart rate during MEBT", x = "Heart Rate (bpm)", y = "RPE")

```


## Heart rate percentage and symptom change over 12 weeks
```{r}

long_techs_sub <- long_techs_sub |>
  mutate(participant = case_when(
    participant == "techs_03" ~ "03",
    participant == "techs_10" ~ "10",
    participant == "techs_11" ~ "11",
    participant == "techs_12" ~ "12",
    participant == "techs_15" ~ "15",
    participant == "techs_19" ~ "19",
    participant == "techs_25" ~ "25",
    participant == "techs_26" ~ "26",
    participant == "techs_27" ~ "27",
    participant == "techs_34" ~ "34",
    participant == "techs_35" ~ "35",
    participant == "techs_37" ~ "37",
    TRUE ~ participant
  )) |>
  mutate(participant = factor(participant, levels = c("03", "10", "11", "12", "15", "19", "25", "26", "27", "34", "35", "37")))




ggplot(long_techs_sub, aes(x = time_point, y = heart_rate, group = participant)) +
  # Main heart rate line (most pronounced)
  geom_line(color = "#f57600", size = 1) +
  geom_point(color = "#f57600", size = 1.5) + 
  
  # Main symptom change line (most pronounced)
  geom_line(aes(group = participant, y = symptom_change*20), na.rm = TRUE, 
            color = "blue", size = 1) + 
  geom_point(aes(group = participant, y = symptom_change*20), na.rm = TRUE, 
             color = "blue", size = 1.5) + 
  # Background rectangle
  geom_rect(data = long_techs_sub, aes(xmin = 0, xmax = 8, ymin = maxhr_65, ymax = maxhr_80),
            fill = "grey80", alpha = 0.10) + 
  scale_y_continuous(name = "Heart rate", limits = c(-50, 225),
    sec.axis = sec_axis(~./27, name = "Change in severity scores", breaks = seq(-6,9,by = 1))) +
  facet_wrap(~ participant, nrow = 2) +  # Assuming 12 participants, arrange them in 3 rows
  geom_rect(data = long_techs_sub, aes(xmin = 0, xmax = 8, ymin = maxhr_65, ymax = maxhr_80),fill = "grey80", alpha = 0.10) + 
  theme(panel.grid.major = element_line(color = "grey"),
    panel.grid.major.y = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom", legend.key.size = unit(0.5, "cm"),
    axis.title.y.right = element_text(margin = margin(l = 10)),
    text = element_text(size= 12, family = "Times New Roman"),
    panel.background = element_rect(fill = "white", color = "black")) +
 labs(x = "Time Point", y = "Heart Rate", title = "Aerobic participants < 44.5 days since injury") + 
  geom_segment(aes(x = 0, xend = 8 , y = 60, yend = 60), size = 0.5, color = "black", linetype = "dashed")


## SPLIT BETWEEN GROUPS

ggplot(long_techs, aes(x = time_point, y = heart_rate_perc, group = participant)) +
  # Main heart rate line (most pronounced)
  geom_line(color = "#FF9245", size = 1) +
  geom_point(color = "#FF9245", size = 1.5) + 
  
  # Main symptom change line (most pronounced)
  geom_line(aes(group = participant, y = symptom_change*17), na.rm = TRUE, 
            color = "#00A7E1", size = 1) + 
  geom_point(aes(group = participant, y = symptom_change*17), na.rm = TRUE, 
             color = "#00A7E1", size = 1.5) + 
  scale_y_continuous(name = "HR max % (averaged across 36 interventions)", limits = c(-20, 100),
    sec.axis = sec_axis(~./10, name = "Change in Symptom Score (CIF)", breaks = seq(-6,9,by = 1))) +
  facet_wrap(~ participant, nrow = 2) +  # Assuming 12 participants, arrange them in 3 rows
  geom_rect(data = long_techs, aes(xmin = 0, xmax = 8, ymin = maxhr_65, ymax = maxhr_80),fill = "grey80", alpha = 0.10) + 
  theme(panel.grid.major = element_line(color = "grey"),
    panel.grid.major.y = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom", legend.key.size = unit(0.5, "cm"),
    axis.title.y.right = element_text(margin = margin(l = 10)),
    axis.title.y.left = element_text(margin = margin(r = 10)),
    axis.title.x.bottom = element_text(margin = margin(t = 10)),
    text = element_text(size= 12, family = "helvetica"),
    panel.background = element_rect(fill = "white", color = "black")) +
  labs(x = "Time Point During Intervention", y = "Heart Rate (averaged across 36 interventions)", title = "HR Max % and Concussion Symptoms over 12-week intervention") + 
  geom_segment(aes(x = 0, xend = 8 , y = 30, yend = 30), size = 0.5, color = "#00A7E1", linetype = "dashed") +
  geom_segment(aes(x = 0, xend = 8 , y = 80, yend = 80), size = 0.5, color = "#FF9245", linetype = "dashed")

```


## HR and symptoms of participants with highest symptoms
```{r}

long_techs_p <- long_techs |> dplyr::filter(participant %in% c("10", "11", "12", "19", "27", "34"))

ggplot(long_techs_p, aes(x = time_point, y = heart_rate, group = participant)) +
  # Main heart rate line (most pronounced)

  # Additional heart rate averages (more transparent)
  geom_line(aes(y = heart_rate_mon1), color = "#DC2C25", alpha = 0.6, size = 0.8, linetype = "dashed") +
  geom_point(aes(y = heart_rate_mon1), color = "#DC2C25", alpha = 0.6, size = 0.8) +
  
  geom_line(aes(y = heart_rate_mon2), color = "#39631C", alpha = 0.8, size = 0.8, linetype = "dotted") +
  geom_point(aes(y = heart_rate_mon2), color = "#39631C", alpha = 0.8, size = 0.8) +
  
  geom_line(aes(y = heart_rate_mon3), color = "#07509B", alpha = 0.6, size = 0.8, linetype = "dotdash") +
  geom_point(aes(y = heart_rate_mon3), color = "#07509B", alpha = 0.6, size = 0.8) +
  
  # Additional symptom change averages (more transparent, scaled by 15)
  geom_line(aes(y = symptom_change_mon1*20), color = "#DC2C25", alpha = 0.6, size = 0.8, linetype = "dashed") +
  geom_point(aes(y = symptom_change_mon1*20), color = "#DC2C25", alpha = 0.6, size = 0.8) +
  
  geom_line(aes(y = symptom_change_mon2*20), color = "#39631C", alpha = 0.8, size = 0.8, linetype = "dotted") +
  geom_point(aes(y = symptom_change_mon2*20), color = "#39631C", alpha = 0.8, size = 0.8) +
  
  geom_line(aes(y = symptom_change_mon3*20), color = "#07509B", alpha = 0.6, size = 0.8, linetype = "dotdash") +
  geom_point(aes(y = symptom_change_mon3*20), color = "#07509B", alpha = 0.6, size = 0.8) +
  
  # Background rectangle
  geom_rect(data = long_techs_p, aes(xmin = 0, xmax = 7, ymin = maxhr_65, ymax = maxhr_80),
            fill = "grey80", alpha = 0.10) + 
  scale_y_continuous(name = "Heart rate", limits = c(-50, 225),
    sec.axis = sec_axis(~./20, name = "Change in severity scores", breaks = seq(-6,9,by = 3))) +
  facet_wrap(~ participant, nrow = 1) +  # Assuming 12 participants, arrange them in 3 rows
  geom_rect(data = long_techs_p, aes(xmin = 0, xmax = 8, ymin = maxhr_65, ymax = maxhr_80),fill = "grey80", alpha = 0.10) + 
  theme(panel.grid.major = element_line(color = "grey"),
    panel.grid.major.y = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom", legend.key.size = unit(0.5, "cm"),
    axis.title.y.right = element_text(margin = margin(l = 10)),
    text = element_text(size= 12, family = "Times New Roman"),
    panel.background = element_rect(fill = "white", color = "black")) +
  labs(x = "Time Point During Intervention", y = "Heart Rate", title = "
  Monthly mean heart rate and severity score change for aerobic 
  participants significantly over HR threshold or symptomatic within first month") + 
   geom_segment(aes(x = 0, xend = 8 , y = 60, yend = 60), size = 0.5, color = "black", linetype = "dashed")

```



## Differences in outcome based on adherence
```{r}
Techs$adherence <- as.factor(Techs$adherence)
Techs$annual_income <- as.numeric(Techs$annual_income)

Techs1 <- Techs[-c(20),]

t.test(Techs1$num_symp_baseline ~ Techs1$adherence, na.rm = TRUE)
sd(Techs$days_since_injury[Techs$adherence == "Completed"],na.rm = TRUE)
sd(Techs$days_since_injury[Techs$adherence == "Dropped out"],na.rm = TRUE)


prop.test(table(Techs$annual_income, Techs$adherence))

levels(Techs$adherence) <- c("Completed","Dropped out")

Techs%>%ggplot(aes(x=adherence, y = baseline_cif, na.omit())) + 
  geom_boxplot(width=0.5,lwd=1.0, aes(fill=adherence), outlier.size = 0) + geom_point()

prop_df <- data.frame(Category = c("Completed","Dropped out"),
                      Proportion = c(0.5833333, 0.75))
ggplot(prop_df, aes(x = Category, y = Proportion)) +
  geom_bar(stat = "identity", aes(fill = Category))
```



## Heart rate and symptom severity correlation 
```{r}


spearman <- long_techs %>% 
  filter(time_point %in% c("min05", "min10", "min15", "min20", "min25")) |> 
  group_by(participant) |>
  summarize(
    Correlation = cor(heart_rate_mon3, symptom_change_mon3, 
                      method = 'spearman', 
                      use = 'complete.obs'))

print(spearman, short = FALSE)

```
 
 
## Data wrangling for mixed effects models
```{r}
Techs_long <- Techs |> filter(randomization_group == 0) |> mutate(baseline_vig_and_mod = baseline_vig_min_per_day_pa + baseline_mod_min_pa)

Techs_long_hr <- Techs_long %>%
  dplyr::select(participant, relative_vo2max_agecorrected_baseline, age, adherence, days_since_injury_calc,baseline_vig_and_mod, 
                matches("baseline_hr_int1_.*") & !contains("hr_max"), 
                matches("hr_.*_int1_d5") & !contains("hr_max")) %>%
  pivot_longer(cols = -c(participant, relative_vo2max_agecorrected_baseline, age, days_since_injury_calc,baseline_vig_and_mod, adherence),
               names_to = "time",
               values_to = "HR")
                
Techs_long_symp <- Techs_long %>%
  dplyr::select(participant,matches(".*_cif_int.*")) %>%
  pivot_longer(cols = -participant,
               names_to = "times",
               values_to = "symptoms")|>
    dplyr::select(symptoms)
                

Techs_long <- bind_cols(Techs_long_hr, Techs_long_symp)


Techs_long <- Techs_long %>%
  mutate(
    intervention = case_when(
      grepl("baseline_hr_int1_d5_d\\d+", time) ~ as.numeric(gsub("baseline_hr_int1_d5_d(\\d+)", "\\1", time)),
      grepl("hr_\\d+_int1_d5_d\\d+", time) ~ as.numeric(gsub("hr_\\d+_int1_d5_d(\\d+)", "\\1", time)),
      grepl("hr_.*_int1_d5", time) ~ 1,
      grepl("baseline_hr_int1_d5", time) ~ 1,
      TRUE ~ NA_real_
    ),
    collection = case_when(
      grepl("baseline_hr_int1_d5_.*", time) ~ 0,
      grepl("hr_\\d+_int1_d5.*", time) ~ as.numeric(gsub("hr_(\\d+)_int1_d5.*", "\\1", time)),
      TRUE ~ NA_real_
    ),
   month = case_when(
  intervention >= 1 & intervention <= 12 ~ 1,
  intervention >= 13 & intervention <= 24 ~ 2,
  intervention >= 25 & intervention <= 36 ~ 3,
  TRUE ~ NA_real_
)) |>
      dplyr::select(-time)
```
 

## HR and symptoms mixed effects models
```{r}
techs_lme <- lmerTest::lmer(symptoms ~ HR* + (1 + month|participant:collection),data = Techs_long)

summary(techs_lme)

tab_model(techs_lm, digits = 4, digits.re = 4, show.df = TRUE, df.method = "satterthwaite")

anova(techs_lme,techs_lme1)

jn_intervals <- probe_interaction(techs_lme, 
                                 pred = adherence, 
                                 modx = as.factor(month),   # Third variable
                                 alpha = .05, 
                                 ci = 0.95,plot.points = TRUE,size = 4, fdr = TRUE, se = TRUE)

print(jn_intervals, digits = 6)
```
 
 
## Adherence x symptom severity
```{r}
techs_lm <- lm(symptoms ~ adherence,data = Techs_long)

summary(techs_lm)

ggplot(data = Techs_long, aes(x = adherence, y = symptoms)) + 
  geom_point() + 
  geom_smooth(method = "lm") +
  labs(x = "Adherence % rate", y = "Symptoms severity") +
  theme_classic()
```
 
 